---
title: "The effect of tarrif reduction on consumer price"
author: "Dor Meir"
date: "August 22, 2019"
output:
  pdf_document:
    toc: yes
    toc_float: true
    toc_depth: '3'

---

<Setting up things>

```{r setup, include=FALSE}
#install.packages("estout")
library(haven)
#install.packages("plm")
library(plm)
### TUNA
tuna <- read_dta("stata_tuna_with_sardines_without_sardin_and_tuna_outliers.dta")
tuna<-pdata.frame(tuna,index=c("brand_number","date"),drop.index = TRUE, row.names = TRUE)
## Drop strong outliers:
# Sardin:
# filtuna prices evenly range from 0.55 NIS/kg to 162 NIS/kg, which both are very unlikely:
tuna<-subset(tuna,!(sardin==1&brand_name=="filtuna_m_big"))
# wilifood prices range from 26.68 NIS/kg (reasonble) to 136 NIS/kg (very unreasonable), with a mean of 78 (Other products mean are 41) :
tuna<-subset(tuna,!(sardin==1&brand_name=="wilifood_m_big"))
#tuna<-subset(tuna,!(sardin==1&brand_name=="private_brand_m_big"))
# observations of same brand who are less than 8 NIS/Kg:
#tuna$price_nom[tuna$tuna==1&tuna$price_nom<8]=NA
# Tuna:
# The mean is 36.68 NIS/Kg, but these observations:
# 136 NIS/Kg:
tuna$price_nom["57-382018"]=NA
# 323 NIS/Kg:
tuna$price_nom["46-42015"]=NA
# 9 observation of same brand who are less than 8 NIS/Kg:
tuna$price_nom[tuna$tuna==1&tuna$price_nom<8]=NA
# observations which are more than 60 NIS/Kg:
#tuna$price_nom[tuna$tuna==1&tuna$price_nom>60]=NA
#tuna<-subset(tuna,!(tuna==1&brand_name=="man_ugiot_i"))
### Oil
oil <- read_dta("stata_oil_with_cooking_without_outliers.dta")
# Converting to pdata.frame (a panel data with both individual and time index), so that we won't have to use the index paramter on the plm command (like xtset in stata)
oil<-pdata.frame(oil,index=c("brand_number","date"),drop.index = TRUE, row.names = TRUE)
### Cheese
cheese <- read_dta("stata_cheese_with_white_without_outliers.dta")
colnames(cheese)[6]="date_stata_time"
#cheese$price_nom[which(cheese$price_nom==-Inf)]=NA
cheese <- cbind(cheese, date_backup=cheese$date_n)
cheese <- cbind(cheese, lprice_nom=log(cheese$price_nom))
cheese<-pdata.frame(cheese,index=c("brand_number","date_n"),drop.index = TRUE, row.names = TRUE)
colnames(cheese)[40]="date_n"
cheese$lprice_nom[which(cheese$lprice_nom==-Inf)]=NA
cheese$price_nom[which(cheese$price_nom==-Inf)]=NA
## Panel Data Linear Model package:
#install.packages("plm")
#install.packages("coeftest")

#Setup stata commands:
#install.packages('RStata')
#options("RStata.StataPath" = "C:/Users/Dor Meir/Documents/stata14/stata14")
#options("RStata.StataVersion" = 14.2)

#install.packages("sandwich")
library(sandwich)
#install.packages("lmtest")
library("lmtest")
#install.packages("stargazer")
#library("stargazer")
#install.packages("tidyverse")
#library("tidyverse")
require(ggplot2)
library(tree)
#install.packages("DataCombine")
#library("DataCombine")
#install.packages("tibble")
```

# Data exploration - graphs of nominal price

```{r data exploration, echo=FALSE,message=FALSE, warning=FALSE, results=TRUE}
## TUNA
library(tibble)
#library(tidyverse) # for data wrangling and plotting
library(svglite) # for better looking plots
library(kableExtra) # for better looking tables
library(RefManageR) # for referencing
library(truncnorm) # for drawing from a truncated normal distribution
library(tidymodels) # for modelling
library(knitr) # for presenting tables
library(mlbench) # for the Boston Housing data
library(ggdag) # for plotting DAGs
tuna_tibble <-as_tibble(tuna)
tuna_tibble %>% select(brand_name, price_nom, date_n, month, year, tuna, sardin)
tuna$date_n_factor <- as.factor(tuna$date_n)
p <- ggplot(data = tuna, aes(x = date_n_factor, y = price_nom , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ sardin) + ggtitle("Tuna (left) & Sardin (right) cans monthly prices over ~3.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(20, 60))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ sardin) + ggtitle("A closer look: Tuna (left) & Sardin (right) cans monthly prices over ~3.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# log price
p <- ggplot(data = tuna, aes(x = date_n_factor, y = lprice_nom , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ sardin) + ggtitle("Tuna (left) & Sardin (right) cans monthly prices over ~3.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(3, 4))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ sardin) + ggtitle("A closer look: Tuna (left) & Sardin (right) cans monthly prices over ~3.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
## OIL
oil_tibble <-as_tibble(oil)
oil_tibble %>% select(brand_name, price_nom, date_n, month, year, olive, cooking_oil)
oil$date_n_factor <- as.factor(oil$date_n)
p <- ggplot(data = oil, aes(x = date_n_factor, y = price_nom , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ cooking_oil) + ggtitle("Olive (left) & Cooking (right) oils monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(5, 60))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ cooking_oil) + ggtitle("A closer look: Olive (left) & Cooking (right) oils monthly prices over 2.34 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# log price
p <- ggplot(data = oil, aes(x = date_n_factor, y = lprice_nom , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ cooking_oil) + ggtitle("Olive (left) & Cooking (right) oils monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(2, 4))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ cooking_oil) + ggtitle("A closer look: Olive (left) & Cooking (right) oils monthly prices over 2.34 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
## Cheese
cheese_tibble <-as_tibble(cheese)
cheese_tibble %>% select(brand_name, price_nom, date_n, month, year, yellow, white_cheese)
cheese$date_n_factor <- as.factor(cheese$date_n)
p <- ggplot(data = cheese, aes(x = date_n_factor, y = price_nom , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ white_cheese) + ggtitle("White (left) & Yellow (right )cheeses monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(20, 70))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ white_cheese) + ggtitle("A closer look: Yellow (left) and White (right) cheeses monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# log price
p <- ggplot(data = cheese, aes(x = date_n_factor, y = lprice_nom , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ white_cheese) + ggtitle("White (left) & Yellow (right )cheeses monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(2.5, 5))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ white_cheese) + ggtitle("A closer look: Yellow (left) and White (right) cheeses monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
```

# Tree models

"At every node, a set of possible split points is identified for every predictor variable. The algorithm calculates the improvement in purity of the data that would be created by each split point of each variable. The split with the greatest improvement is chosen to partition the data and create child nodes."

```{r trees, include=TRUE}
tuna_tree <- tree( price_nom ~ jan2015reduc + jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna , tuna)
plot(tuna_tree)
text(tuna_tree)
oil_tree <- tree( price_nom ~ jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive , oil)
plot(oil_tree)
text(oil_tree)
cheese_tree <- tree(price_nom ~ jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, cheese)
#plot(cheese_tree)
#text(cheese_tree)
summary(cheese_tree)
```

_No good split was found in the cheese tarrif reduction model!_

# Linear Models

## Random Effects Models
### Random Effects full model (close to stata default panel data model)

```{r random effects, include=TRUE}
tuna_re_full <- plm(price_nom ~  jan2015reduc + jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna, effect="twoways", model = "random")
#stargazer(tuna_re_full)
nobs(tuna_re_full)
coeftest(tuna_re_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_re_full <- plm(price_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil, effect="twoways",model = "random") 
nobs(oil_re_full)
coeftest(oil_re_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_re_full <- plm(price_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, data = cheese, effect="twoways",model = "random") 
nobs(cheese_re_full)
coeftest(cheese_re_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

That's the closest I got to the stata result of:
xtreg price_nom jan2015reduc jan2015reduc_tuna jan2016reduc jan2016reduc_tuna, re
it is actually closer to:
xtreg price_nom jan2015reduc jan2015reduc_tuna jan2016reduc jan2016reduc_tuna, sa
-> which is the the Random Effect small-sample Swamy–Arora estimator individual-level variance component.

### Random Effects - most significant time frames

The full Random effect model in the timeframes which give the most significant results (without cheese, which is insignificant):

```{r most significant random-effects, include=TRUE}
tuna$lsalary_industry_worker<-log(tuna$salary_industry_worker)
oil$lsalary_industry_worker<-log(oil$salary_industry_worker)
cheese$lsalary_industry_worker<-log(cheese$salary_industry_worker)

tuna_signif <- subset(tuna,date_n<382017)
tuna_re_full_significant <- plm(price_nom ~  jan2015reduc + jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_re_full_significant, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_signif <- subset(oil,year<2018)
oil_re_full_significant <- plm(price_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_re_full_significant, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_signif <- subset(cheese,date_n<382017)

```

## Fixed effects models

### Fixed effect full model

Fixed effect is preffered since it has no prior assumption on the unobserved individual effect ci, and this effect may be correlated with the explantory variable (fixed effects assumption).
Nothing is significant with the exception of tuna, but this significance might be a results of ommitting the jan2015reduc_tuna dummy, which is dropped because of singularities.
Note that *in the fe model, the time-invariant regressors cancel!* - which means that the reduction dummy's (jan2015reduc, etc...) will cancel out.
*I believe they are failing due to the dummy variable trap!*


```{r fixed effects, include=TRUE}
tuna_fe_full <- plm(price_nom ~  jan2015reduc + jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna, effect="twoways",model = "within")
coeftest(tuna_fe_full, vcov.=function(x) vcovHC(x,type="sss",cluster="group"));within_intercept(tuna_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
summary(tuna_fe_full)
oil_fe_full <- plm(price_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil, effect="twoways",model = "within") 
coeftest(oil_fe_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(oil_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_fe_full <- plm(price_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, data = cheese, effect="twoways",model = "within") 
coeftest(cheese_fe_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(cheese_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

Let's check for linear dependency in the tuna fe model:

```{r checking for linear dependency, include=TRUE}
alias(tuna_fe_full)
```

As you can see, jan2015reduc is linear depenedent in jan2015reduc_tuna, and there for it's effect cannot be identified.
Let's omit the jan2015reduc variable, and run the model again:

```{r tuna fixed effects without jan2015reduc, include=TRUE}
tuna_fe_full_not_linear <- plm(price_nom ~  jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna, effect="twoways",model = "within")
coeftest(tuna_fe_full_not_linear, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full_not_linear,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
summary(tuna_fe_full_not_linear)
```

Now we don't have linear dependencies, and **jan2016reduc_tuna positive effect was found significant to the level of 5%.** some from now one the tuna FE model will omit the jan2015reduc variable.
(switching between jan2015reduc and jan2015reduc_tuna gives the sames exact estimator for both of them - another proof the of linear dependence between the two)

### Fixed effect full model - most significant time frames

```{r most significant fixed-effects, include=TRUE}
tuna_fe_full_significant <- plm(price_nom ~  jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "within")
coeftest(tuna_fe_full_significant, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full_significant,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_fe_full_significant <- plm(price_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "within") 
coeftest(oil_fe_full_significant, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(oil_fe_full_significant,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

This time the jan2016reduc in oil became significant.

## Hausman Test: Random Effects Vs. Fixed effects
We'll use the Hausman Test for Panel Models in order to determine which model suits best the data - fixed effect or random effect:
```{r Hausman Test, include=TRUE}
phtest(tuna_fe_full,tuna_re_full)
phtest(oil_fe_full,oil_re_full)
phtest(cheese_fe_full,cheese_re_full)
phtest(tuna_fe_full_significant,tuna_re_full_significant)
phtest(oil_fe_full_significant,oil_re_full_significant)
```
*The tuna and cheese models corresponds to random effect, while the oil corresponds to fixed effects.*

# Log-Linear Models

These models are the exact same one from before, except the explained variable, the nominal price, is not transformed into ln(nominal price).

## Random Effects

### Random Effects full model (close to stata default panel data model)

```{r log random effects, include=TRUE}
tuna_lre_full <- plm(lprice_nom ~  jan2015reduc + jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna, effect="twoways",model = "random")
coeftest(tuna_lre_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_lre_full <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil, effect="twoways",model = "random") 
coeftest(oil_lre_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_lre_full <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, data = cheese, effect="twoways",model = "random") 
coeftest(cheese_lre_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### Random Effects - most significant time frames

```{r most significant log random-effects, include=TRUE}
tuna_signif <- subset(tuna,date_n<382017)
cheese_signif <- subset(cheese,date_n<382017)


tuna_lre_full_significant <- plm(lprice_nom ~  jan2015reduc + jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_lre_full_significant, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_signif <- subset(oil,year<2018)
oil_lre_full_significant <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_lre_full_significant, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_lre_full_significant <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, data = cheese_signif, effect="twoways",model = "random") 
coeftest(cheese_lre_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

## Fixed Effects models
### Fixed effect full model

```{r log fixed effects, include=TRUE}
tuna_lfe_full <- plm(lprice_nom ~  jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna, effect="twoways",model = "within")
coeftest(tuna_lfe_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_lfe_full <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil, effect="twoways",model = "within") 
coeftest(oil_lfe_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_lfe_full <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, data = cheese, effect="twoways",model = "within") 
coeftest(cheese_lfe_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

**In comparison to the linear fixed-effects model,
the log-linear fixed-effects models of cheese returned significant results:
the jan2016reduc_yellow negative effect was significant to the level of 6%.**

### Fixed effect full model - most significant time frames

```{r most significant log fixed-effects, include=TRUE}
tuna_lfe_full_significant <- plm(lprice_nom ~  jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "within")
coeftest(tuna_lfe_full_significant, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_lfe_full_significant <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "within") 
coeftest(oil_lfe_full_significant, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_lfe_full <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, data = cheese_signif, effect="twoways",model = "within") 
coeftest(cheese_lfe_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"));within_intercept(tuna_fe_full,vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

## Hausman Test: Random Effects Vs. Fixed effects
```{r log-linear Hausman Test, include=TRUE}
phtest(tuna_lfe_full,tuna_lre_full)
phtest(oil_lfe_full,oil_lre_full)
phtest(cheese_lfe_full,cheese_lre_full)
phtest(tuna_lfe_full_significant,tuna_lre_full_significant)
phtest(oil_lfe_full_significant,oil_lre_full_significant)
```
The p-value much is bigger than 0.05 on all tests ->>
*All of the models are significantly more suited for the random effects settings.*
_So from now on we'll continue only with the random effects._

## Random Effects models with lags

### full log model with lead and lags

```{r log random effects with lead and lags, include=TRUE}
#tuna
tuna_lre_full_lags <- plm(lprice_nom ~  jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,1) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,1) , data = tuna, effect="twoways",model = "random")
coeftest(tuna_lre_full_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
#oil
oil_lre_full_lags <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,1) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,1) , data = oil, effect="twoways",model = "random") 
coeftest(oil_lre_full_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# Cheese
cheese_lre_full_lags <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,1) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,1) , data = cheese, effect="twoways",model = "random")
coeftest(cheese_lre_full_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### Random Effect full log model with significant lead and lags

Now, let's try model only the significant leads and lags:

```{r log random effect with only significant lead and lags, include=TRUE}
#tuna
tuna_lre_full_lags <- plm(lprice_nom ~  jan2015reduc  + jan2015reduc_tuna +  + jan2016reduc + jan2016reduc_tuna + lag(jan2016reduc_tuna,1) , data = tuna, effect="twoways",model = "random")
coeftest(tuna_lre_full_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
#oil
oil_lre_full_lags <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive  , data = oil, effect="twoways",model = "random") 
coeftest(oil_lre_full_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# Cheese
cheese_lre_full_lags <- plm(lprice_nom ~  jan2016reduc +  jan2016reduc_yellow + lag(jan2016reduc_yellow,1) + jan2017reduc + jan2017reduc_yellow  , data = cheese, effect="twoways",model = "random")
coeftest(cheese_lre_full_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

**To sum up: adding only the significant leads and lags led to:
1. Tuna (& sardins) - no significant effect of tarrif reduction on price
2. Oil - significant effect of tarrif reduction on both olive and cooking price
3. Cheese - sinigicant effect of tarrif reduction on yellow price in jan2016
These results are quite similiar to the results of the model without the leads and lags**

### random effect, Add covariates, without lead and lags

```{r log fixed-effects with with covariates, include=TRUE}
#tuna
tuna_lre_covariates_lags <- plm(lprice_nom ~  jan2015reduc_tuna + jan2016reduc + lag(jan2016reduc,5) + jan2016reduc_tuna + lag(jan2016reduc_tuna,5) + proccess_fish_p2012 +  salary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_lre_covariates_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
#oil
oil_lre_covariates_lags <- plm(lprice_nom ~ lead(jan2016reduc,1) + jan2016reduc + lag(jan2016reduc,1) + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive + proccess_oil_p2012 +  salary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_lre_covariates_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# Cheese
cheese_lre_covariates_lags <- plm(lprice_nom ~  jan2016reduc + lag(jan2016reduc,2) + jan2016reduc_yellow + jan2017reduc + lag(jan2017reduc,3) + jan2017reduc_yellow + proccess_milk_products_p2012 , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_lre_covariates_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
**The covariates are insignificant...**

### random effect, Add covariates, with lead and lags

```{r log fixed-effects with covariates and lead and lags, include=TRUE}
#tuna
tuna_lre_covariates_lags <- plm(lprice_nom ~  jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,1) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,1) + proccess_fish_p2012 +  salary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_lre_covariates_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
#oil
oil_lre_covariates_lags <- plm(lprice_nom ~ jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,1) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,1) + proccess_oil_p2012 +  salary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_lre_covariates_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# Cheese
cheese_lre_covariates_lags <- plm(lprice_nom ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,1) + jan2017reduc + lead(jan2017reduc_yellow,1) + proccess_milk_products_p2012 , effect="twoways", data = cheese_signif,model = "random")
coeftest(cheese_lre_covariates_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

## Net price -  price minus raw material cost (Random effects only)

The explained is the consumer price minus material cost or cost of prduct in a country which is a main exporter to Israel
```{r net price setup, echo=FALSE,message=FALSE, warning=FALSE, results=TRUE}
### TUNA
# The net price of tuna:
tuna$price_net <- tuna$price_nom
tuna$price_net[tuna$tuna==1] <- tuna$price_nom[tuna$tuna==1] - tuna$thai_price[tuna$tuna==1]
# The net price of sardin:
tuna$price_net[tuna$sardin==1] <- tuna$price_nom[tuna$sardin==1] - tuna$"sardin_latvia"[tuna$sardin==1]
tuna$lprice_net<-log(tuna$price_net)
### OIL
# The net price of olive oil:
oil$price_net <- oil$price_nom
oil$price_net[oil$olive==1] <- oil$price_nom[oil$olive==1] - oil$it_sp_price[oil$olive==1]
# The net price of cooking oil:
oil$price_net[oil$cooking_oil==1] <- oil$price_nom[oil$cooking_oil==1] - oil$cooking_oil_world[oil$cooking_oil==1]
oil$lprice_net<-log(oil$price_net)
# # Cheese
# The net price of yellow cheese:
cheese$price_net <- cheese$price_nom
cheese$price_net[cheese$yellow==1] <- cheese$price_nom[cheese$yellow==1] - cheese$pl_price[cheese$yellow==1]

# The net price of white cheese:
cheese$price_net[cheese$white_cheese==1] <- cheese$price_nom[cheese$white_cheese==1] - cheese$white_poland[cheese$white_cheese==1]
cheese$lprice_net<-log(cheese$price_net)

cheese_signif <- subset(cheese,date_n<382017)
```

### Graphs - net price

```{r net data exploration, echo=FALSE,message=FALSE, warning=FALSE, results=TRUE}
## TUNA
tuna_tibble <-as_tibble(tuna)
tuna_tibble %>% select(brand_name, price_net, date_n, month, year, tuna, sardin)
tuna$date_n_factor <- as.factor(tuna$date_n)
p <- ggplot(data = tuna, aes(x = date_n_factor, y = price_net , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ sardin) + ggtitle("Tuna (left) & Sardin (right) cans monthly prices over ~3.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# log price
p <- ggplot(data = tuna, aes(x = date_n_factor, y = lprice_net , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ sardin) + ggtitle("Tuna (left) & Sardin (right) cans monthly prices over ~3.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(3, 4))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ sardin) + ggtitle("A closer look: Tuna (left) & Sardin (right) cans monthly prices over ~3.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
## OIL
oil_tibble <-as_tibble(oil)
oil_tibble %>% select(brand_name, price_net, date_n, month, year, olive, cooking_oil)
oil$date_n_factor <- as.factor(oil$date_n)
p <- ggplot(data = oil, aes(x = date_n_factor, y = price_net , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ cooking_oil) + ggtitle("Olive (left) & Cooking (right) oils monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# log price
p <- ggplot(data = oil, aes(x = date_n_factor, y = lprice_net , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ cooking_oil) + ggtitle("Olive (left) & Cooking (right) oils monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(1.25, 3.5))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ cooking_oil) + ggtitle("A closer look: Olive (left) & Cooking (right) oils monthly prices over 2.34 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
## Cheese
cheese_tibble <-as_tibble(cheese)
cheese_tibble %>% select(brand_name, price_net, date_n, month, year, yellow, white_cheese)
cheese$date_n_factor <- as.factor(cheese$date_n)
p <- ggplot(data = cheese, aes(x = date_n_factor, y = price_net , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ white_cheese) + ggtitle("White (left) & Yellow (right )cheeses monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# log price
p <- ggplot(data = cheese, aes(x = date_n_factor, y = lprice_net , group = brand_name,color=brand_name))
p + geom_point() + stat_smooth(aes(group = 1)) + stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ white_cheese) + ggtitle("White (left) & Yellow (right )cheeses monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
# And a closer look:
p + geom_point() + stat_smooth(aes(group = 1)) + coord_cartesian(ylim =c(3, 4))+ stat_summary(aes(group = 1), geom = "point", fun.y = mean, shape = 30, size = 3) + facet_grid(. ~ white_cheese) + ggtitle("A closer look: Yellow (left) and White (right) cheeses monthly prices over ~2.25 years") + theme(text = element_text(size=8),axis.text.x = element_text(angle=90, hjust=1),legend.position = "none") + geom_vline(xintercept = c(5,17), color = "black", size=0.5)
```



```{r net price, include=TRUE}
### TUNA
tuna_signif <- subset(tuna,date_n<382017)
cheese_signif <- subset(cheese,date_n<382017)

# The model
tuna_net_lre_lags <- plm(lprice_net ~  jan2015reduc_tuna + jan2016reduc +  jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_signif <- subset(oil,year<2018)
# The model
oil_net_lre_lags <- plm(lprice_net ~ jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_signif <- subset(cheese,date_n<382017)
# The model
cheese_net_lre_lags <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### Net price, with covariates 

```{r net price with covariates, include=TRUE, warning=FALSE}
### TUNA
tuna_net_lre_covariates <- plm(lprice_net ~  jan2015reduc + jan2015reduc_tuna + jan2016reduc +  jan2016reduc_tuna + proccess_fish_p2012 +  salary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_covariates, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_covariates <- plm(lprice_net ~ jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive + proccess_oil_p2012 +  salary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_covariates, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_covariates <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow + proccess_milk_products_p2012 , data = cheese, effect="twoways",model = "random")
coeftest(cheese_lre_covariates_lags, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

**The covariates are insignificant!**

## Net price, no leads and lags

```{r net price without covariates, include=TRUE, warning=FALSE}
### TUNA
tuna_net_lre_covariates <- plm(lprice_net ~  jan2015reduc + jan2015reduc_tuna + jan2016reduc +  jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_covariates, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_covariates <- plm(lprice_net ~ jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_covariates, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_covariates <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow, data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_covariates, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

## Net price, with lead and lags

### lag = 1

```{r net price with lead and lags 1, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lead(jan2015reduc_tuna,1) + lag(jan2015reduc,1) + lag(jan2015reduc_tuna,1) + lead(jan2016reduc,1) + lead(jan2016reduc_tuna,1)+ lag(jan2016reduc,1) + lag(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,1) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,1) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,1), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lag = 1 without lead

```{r net price with lead and lags 1 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,1) + lag(jan2015reduc_tuna,1) + lag(jan2016reduc,1) + lag(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,1) + lag(jan2016reduc_olive,1) + lag(jan2017reduc,1) + lag(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   lag(jan2016reduc,1) + lag(jan2016reduc_yellow,1) + lag(jan2017reduc,1) + lag(jan2017reduc_yellow,1), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 2

```{r net price with lead and lags 2, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,2) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,2), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,2) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,2), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,2) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,2), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lag = 2 without lag

```{r net price with lags 2, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,2) + lag(jan2015reduc_tuna,2) + lag(jan2016reduc,2) + lag(jan2016reduc_tuna,2), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2016reduc_olive,2) + lag(jan2017reduc,2) + lag(jan2017reduc_olive,2), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,2) + lag(jan2016reduc_yellow,2) + lag(jan2017reduc,2) + lag(jan2017reduc_yellow,2), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 3

```{r net price with lead and lags 3, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,3) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,3), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,3) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,3), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,3) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,3), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lag = 3 without lag

```{r net price with lags 3, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,3) + lag(jan2015reduc_tuna,3) + lag(jan2016reduc,3) + lag(jan2016reduc_tuna,3), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2016reduc_olive,3) + lag(jan2017reduc,3) + lag(jan2017reduc_olive,3), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   lag(jan2016reduc,3) + lag(jan2016reduc_yellow,3) + lag(jan2017reduc,3) + lag(jan2017reduc_yellow,3) + jan2017reduc_yellow + lag(jan2017reduc_yellow,3), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 4

```{r net price with lead and lags 4, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,4) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,4) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,4) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,4), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lag = 4 without lead

```{r net price with  and lags 4, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,4) + lag(jan2015reduc_tuna,4) + lag(jan2016reduc,4) + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2016reduc_olive,4) +lag(jan2017reduc,4) + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,4) + lag(jan2016reduc_yellow,4) +lag(jan2017reduc,4) + lag(jan2017reduc_yellow,4), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 4 without lead with t1

```{r net price with lead and lags 4 without lead, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ jan2015reduc + jan2015reduc_tuna + lag(jan2015reduc_tuna,4) + jan2016reduc + + jan2016reduc_tuna + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc+ jan2016reduc_olive + lag(jan2016reduc_olive,4) + jan2017reduc + jan2017reduc_olive + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   jan2016reduc + jan2016reduc_yellow + lag(jan2016reduc_yellow,4) + jan2017reduc + jan2017reduc_yellow + lag(jan2017reduc_yellow,4), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 4 without lead, without t=1

```{r net price with lead and lags 4 without lead without t1, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,4) + lag(jan2015reduc_tuna,4) + lag(jan2016reduc,4) + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2016reduc_olive,4) + lag(jan2017reduc,4) + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,4) + lag(jan2016reduc_yellow,4) + lag(jan2017reduc,4) + lag(jan2017reduc_yellow,4), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 5

```{r net price with lead and lags 5, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,5) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,5) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,5) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,5), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 5 without lead

```{r net price with only lags 5, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ jan2015reduc + jan2015reduc_tuna + lag(jan2015reduc_tuna,5) + jan2016reduc + jan2016reduc_tuna + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc  + jan2016reduc_olive + lag(jan2016reduc_olive,5) + jan2017reduc + jan2017reduc_olive + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   jan2016reduc + jan2016reduc_yellow + lag(jan2016reduc_yellow,5) + jan2017reduc + jan2017reduc_yellow + lag(jan2017reduc_yellow,5), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
??
### lag = 5 , all of them, without lead
????
```{r net price with only lags 5 all of them , include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ jan2015reduc + jan2015reduc_tuna  + lag(jan2015reduc_tuna,5) + jan2016reduc + lag(jan2016reduc,5) + jan2016reduc_tuna + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc  + lag(jan2016reduc,5) + jan2016reduc_olive + lag(jan2016reduc_olive,5) + jan2017reduc + lag(jan2017reduc,5) + jan2017reduc_olive + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~ jan2016reduc + lag(jan2016reduc,5) + jan2016reduc_yellow + lag(jan2016reduc_yellow,5) + jan2017reduc + lag(jan2017reduc,5) + jan2017reduc_yellow + lag(jan2017reduc_yellow,5), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 5 without lead, only lag

```{r net price with only lags 5, only lag, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,5) + lag(jan2015reduc_tuna,5) + lag(jan2016reduc,5) + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,5) + lag(jan2016reduc_olive,5) + lag(jan2017reduc,5) + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   lag(jan2016reduc,5) + lag(jan2016reduc_yellow,5) + lag(jan2017reduc,5) + lag(jan2017reduc_yellow,5), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 6 without lead

```{r net price with lead and lags 6 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,6) + lag(jan2015reduc_tuna,6) + lag(jan2016reduc,6) + lag(jan2016reduc_tuna,6), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,6) + lag(jan2016reduc_olive,6) + lag(jan2017reduc,6) + lag(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   lag(jan2016reduc,6) + lag(jan2016reduc_yellow,6) + lag(jan2017reduc,6) + lag(jan2017reduc_yellow,6), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 7 without lead

```{r net price with lead and lags 7 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,7) + lag(jan2015reduc_tuna,7) + lag(jan2016reduc,7) + lag(jan2016reduc_tuna,7), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,7) + lag(jan2016reduc_olive,7) + lag(jan2017reduc,7) + lag(jan2017reduc_olive,7), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   lag(jan2016reduc,7) + lag(jan2016reduc_yellow,7) + lag(jan2017reduc,7) + lag(jan2017reduc_yellow,7), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 8 without lead

```{r net price with lead and lags 8 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,8) + lag(jan2015reduc_tuna,8) + lag(jan2016reduc,8) + lag(jan2016reduc_tuna,8), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,8) + lag(jan2016reduc_olive,8) + lag(jan2017reduc,8) + lag(jan2017reduc_olive,8), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   lag(jan2016reduc,8) + lag(jan2016reduc_yellow,8) + lag(jan2017reduc,8) + lag(jan2017reduc_yellow,8), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 9 without lead

```{r net price with lead and lags 9 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,9) + lag(jan2015reduc_tuna,9) + lag(jan2016reduc,9) + lag(jan2016reduc_tuna,9), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,9) + lag(jan2016reduc_olive,9) + lag(jan2017reduc,9) + lag(jan2017reduc_olive,9), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   lag(jan2016reduc,9) + lag(jan2016reduc_yellow,9) + lag(jan2017reduc,9) + lag(jan2017reduc_yellow,9), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 10 without lead

```{r net price with lead and lags 10 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_net ~ lag(jan2015reduc,10) + lag(jan2015reduc_tuna,10) + lag(jan2016reduc,10) + lag(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~ lag(jan2016reduc,10) + lag(jan2016reduc_olive,10) + lag(jan2017reduc,10) + lag(jan2017reduc_olive,10), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_net ~   lag(jan2016reduc,10) + lag(jan2016reduc_yellow,10) + lag(jan2017reduc,10) + lag(jan2017reduc_yellow,10), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```


### Net price with significant lead and lags, version#1

```{r net price with significant lead and lags, include=TRUE}
### TUNA
tuna_net_lre_lags_sig <- plm(lprice_net ~ jan2015reduc_tuna + lag(jan2015reduc_tuna,1) + jan2016reduc + + jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_sig <- plm(lprice_net ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow , data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

**These are some interesting results:
In tuna & sardin, the overall reduction led to a negative effect on the price sardin, but in the tuna market there was a postivie effect on price!
In Olive & Cooking oil, a negetive effect came in 3 months lag in 2016, and while the 2017 reduction led to an increase in cooling oil price, it led to a decrease in coolking oil price/
In Yellow and White cheeses, the 2016 reduction was found to have a negative effect on the net price of yellow cheese with 1 month delay, and the 2017 reduction was also found to have a negative effect on the yellow cheese price, without a delay.**




### Net price with significant lead and lags, version#2

```{r net price with significant lead and lags ver 2, include=TRUE}
### TUNA
tuna_net_lre_lags_sig <- plm(lprice_net ~ jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna + lag(jan2016reduc_tuna, 4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_sig <- plm(lprice_net ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow , data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

## Net price with significant lead and lags AND import interaction dummy

There was no setting under which the tuna 2015 and 2016 effects didn't create a dummy trap, so the two years were seperated in the case of tuna -->

```{r net price with significant lead and lags and import, include=TRUE}
### TUNA
tuna$jan2015reduc_tuna_import <- tuna$jan2015reduc_tuna*tuna$import
tuna$jan2016reduc_tuna_import <- tuna$jan2015reduc_tuna*tuna$import
tuna_signif <- subset(tuna,date_n<382017)
tuna_net_lre_lags_sig_import_2015 <- plm(lprice_net ~ jan2015reduc_tuna +  jan2015reduc_tuna_import, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig_import_2015, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
tuna_net_lre_lags_sig_import_2016 <- plm(lprice_net ~ jan2016reduc_tuna +  jan2016reduc_tuna_import, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig_import_2016, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil$jan2016reduc_olive_import <- oil$jan2016reduc_olive*oil$import
oil$jan2017reduc_olive_import <- oil$jan2017reduc_olive*oil$import
oil_signif <- subset(oil,year<2018)
oil_net_lre_lags_sig_import <- plm(lprice_net ~ jan2016reduc + jan2016reduc_olive +  lag(jan2016reduc_olive,3) + jan2016reduc_olive_import + jan2017reduc + jan2017reduc_olive + jan2017reduc_olive_import, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig_import, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese$jan2016reduc_yellow_import <- cheese$jan2016reduc_yellow*cheese$import
cheese$jan2017reduc_yellow_import <- cheese$jan2017reduc_yellow*cheese$import
cheese_net_lre_lags_sig_import <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + lag(jan2016reduc_yellow,1) + jan2016reduc_yellow_import+ jan2017reduc + jan2017reduc_yellow + lag(jan2017reduc_yellow,1) + jan2016reduc_yellow_import , data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig_import, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_signif <- subset(cheese,date_n<382017)
```

import as an interaction dummy was found not insignificant, and in tuna it was also ommitted due to linearity. import as a regular dummy deleted by the fixed effects estimation(?).


## nom price, with lead and lags

### lag = 1

```{r nom price with lead and lags 1, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,1) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,1) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,1) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,1), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lag = 1 without lead

```{r nom price with lead and lags 1 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,1) + lag(jan2015reduc_tuna,1) + lag(jan2016reduc,1) + lag(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,1) + lag(jan2016reduc_olive,1) + lag(jan2017reduc,1) + lag(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   lag(jan2016reduc,1) + lag(jan2016reduc_yellow,1) + lag(jan2017reduc,1) + lag(jan2017reduc_yellow,1), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 2

```{r nom price with lead and lags 2, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,2) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,2), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,2) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,2), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,2) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,2), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lag = 2 without lag

```{r nom price with lags 2, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,2) + lag(jan2015reduc_tuna,2) + lag(jan2016reduc,2) + lag(jan2016reduc_tuna,2), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2016reduc_olive,2) + lag(jan2017reduc,2) + lag(jan2017reduc_olive,2), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,2) + lag(jan2016reduc_yellow,2) + lag(jan2017reduc,2) + lag(jan2017reduc_yellow,2), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 3

```{r nom price with lead and lags 3, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,3) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,3), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,3) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,3), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,3) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,3), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lag = 3 without lag

```{r nom price with lags 3, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,3) + lag(jan2015reduc_tuna,3) + lag(jan2016reduc,3) + lag(jan2016reduc_tuna,3), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2016reduc_olive,3) + lag(jan2017reduc,3) + lag(jan2017reduc_olive,3), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   lag(jan2016reduc,3) + lag(jan2016reduc_yellow,3) + lag(jan2017reduc,3) + lag(jan2017reduc_yellow,3) + jan2017reduc_yellow + lag(jan2017reduc_yellow,3), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 4

```{r nom price with lead and lags 4, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,4) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,4) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,4) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,4), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lag = 4 without lead

```{r nom price with  and lags 4, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,4) + lag(jan2015reduc_tuna,4) + lag(jan2016reduc,4) + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2016reduc_olive,4) +lag(jan2017reduc,4) + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,4) + lag(jan2016reduc_yellow,4) +lag(jan2017reduc,4) + lag(jan2017reduc_yellow,4), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 4 without lead with t1

```{r nom price with lead and lags 4 without lead, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ jan2015reduc + jan2015reduc_tuna + lag(jan2015reduc_tuna,4) + jan2016reduc + + jan2016reduc_tuna + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  jan2016reduc+ jan2016reduc_olive + lag(jan2016reduc_olive,4) + jan2017reduc + jan2017reduc_olive + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   jan2016reduc + jan2016reduc_yellow + lag(jan2016reduc_yellow,4) + jan2017reduc + jan2017reduc_yellow + lag(jan2017reduc_yellow,4), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 4 without lead, without t=1

```{r nom price with lead and lags 4 without lead without t1, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,4) + lag(jan2015reduc_tuna,4) + lag(jan2016reduc,4) + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2016reduc_olive,4) + lag(jan2017reduc,4) + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,4) + lag(jan2016reduc_yellow,4) + lag(jan2017reduc,4) + lag(jan2017reduc_yellow,4), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 5

```{r nom price with lead and lags 5, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ jan2015reduc + lead(jan2015reduc_tuna,1) + jan2015reduc_tuna + lag(jan2015reduc_tuna,5) + jan2016reduc + lead(jan2016reduc_tuna,1) + jan2016reduc_tuna + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + lag(jan2016reduc_olive,5) + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   jan2016reduc + lead(jan2016reduc_yellow,1) + jan2016reduc_yellow + lag(jan2016reduc_yellow,5) + jan2017reduc + lead(jan2017reduc_yellow,1) + jan2017reduc_yellow + lag(jan2017reduc_yellow,5), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 5 without lead

```{r nom price with only lags 5, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ jan2015reduc + jan2015reduc_tuna + lag(jan2015reduc_tuna,5) + jan2016reduc + jan2016reduc_tuna + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  jan2016reduc  + jan2016reduc_olive + lag(jan2016reduc_olive,5) + jan2017reduc + jan2017reduc_olive + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   jan2016reduc + jan2016reduc_yellow + lag(jan2016reduc_yellow,5) + jan2017reduc + jan2017reduc_yellow + lag(jan2017reduc_yellow,5), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
??
### lag = 5 , all of them, without lead
????
```{r nom price with only lags 5 all of them , include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ jan2015reduc + jan2015reduc_tuna  + lag(jan2015reduc_tuna,5) + jan2016reduc + lag(jan2016reduc,5) + jan2016reduc_tuna + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~  jan2016reduc  + lag(jan2016reduc,5) + jan2016reduc_olive + lag(jan2016reduc_olive,5) + jan2017reduc + lag(jan2017reduc,5) + jan2017reduc_olive + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~ jan2016reduc + lag(jan2016reduc,5) + jan2016reduc_yellow + lag(jan2016reduc_yellow,5) + jan2017reduc + lag(jan2017reduc,5) + jan2017reduc_yellow + lag(jan2017reduc_yellow,5), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 5 without lead, only lag

```{r nom price with only lags 5, only lag, include=TRUE}

### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,5) + lag(jan2015reduc_tuna,5) + lag(jan2016reduc,5) + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,5) + lag(jan2016reduc_olive,5) + lag(jan2017reduc,5) + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   lag(jan2016reduc,5) + lag(jan2016reduc_yellow,5) + lag(jan2017reduc,5) + lag(jan2017reduc_yellow,5), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 6 without lead

```{r nom price with lead and lags 6 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,6) + lag(jan2015reduc_tuna,6) + lag(jan2016reduc,6) + lag(jan2016reduc_tuna,6), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,6) + lag(jan2016reduc_olive,6) + lag(jan2017reduc,6) + lag(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   lag(jan2016reduc,6) + lag(jan2016reduc_yellow,6) + lag(jan2017reduc,6) + lag(jan2017reduc_yellow,6), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 7 without lead

```{r nom price with lead and lags 7 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,7) + lag(jan2015reduc_tuna,7) + lag(jan2016reduc,7) + lag(jan2016reduc_tuna,7), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,7) + lag(jan2016reduc_olive,7) + lag(jan2017reduc,7) + lag(jan2017reduc_olive,7), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   lag(jan2016reduc,7) + lag(jan2016reduc_yellow,7) + lag(jan2017reduc,7) + lag(jan2017reduc_yellow,7), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 8 without lead

```{r nom price with lead and lags 8 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,8) + lag(jan2015reduc_tuna,8) + lag(jan2016reduc,8) + lag(jan2016reduc_tuna,8), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,8) + lag(jan2016reduc_olive,8) + lag(jan2017reduc,8) + lag(jan2017reduc_olive,8), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   lag(jan2016reduc,8) + lag(jan2016reduc_yellow,8) + lag(jan2017reduc,8) + lag(jan2017reduc_yellow,8), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 9 without lead

```{r nom price with lead and lags 9 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,9) + lag(jan2015reduc_tuna,9) + lag(jan2016reduc,9) + lag(jan2016reduc_tuna,9), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,9) + lag(jan2016reduc_olive,9) + lag(jan2017reduc,9) + lag(jan2017reduc_olive,9), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   lag(jan2016reduc,9) + lag(jan2016reduc_yellow,9) + lag(jan2017reduc,9) + lag(jan2017reduc_yellow,9), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

### lag = 10 without lead

```{r nom price with lead and lags 10 without lag, include=TRUE}
### TUNA
tuna_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2015reduc,10) + lag(jan2015reduc_tuna,10) + lag(jan2016reduc,10) + lag(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_nom ~ lag(jan2016reduc,10) + lag(jan2016reduc_olive,10) + lag(jan2017reduc,10) + lag(jan2017reduc_olive,10), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_full <- plm(lprice_nom ~   lag(jan2016reduc,10) + lag(jan2016reduc_yellow,10) + lag(jan2017reduc,10) + lag(jan2017reduc_yellow,10), data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```


### nom price with significant lead and lags, version#1

```{r nom price with significant lead and lags, include=TRUE}
### TUNA
tuna_net_lre_lags_sig <- plm(lprice_nom ~ jan2015reduc_tuna + lag(jan2015reduc_tuna,1) + jan2016reduc + + jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_sig <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow , data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

**These are some interesting results:
In tuna & sardin, the overall reduction led to a negative effect on the price sardin, but in the tuna market there was a postivie effect on price!
In Olive & Cooking oil, a negetive effect came in 3 months lag in 2016, and while the 2017 reduction led to an increase in cooling oil price, it led to a decrease in coolking oil price/
In Yellow and White cheeses, the 2016 reduction was found to have a negative effect on the nom price of yellow cheese with 1 month delay, and the 2017 reduction was also found to have a negative effect on the yellow cheese price, without a delay.**

### nom price with significant lead and lags, version#2

```{r nom price with significant lead and lags ver 2, include=TRUE}
### TUNA
tuna_net_lre_lags_sig <- plm(lprice_nom ~ jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna + lag(jan2016reduc_tuna, 4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_sig <- plm(lprice_nom ~  jan2016reduc + lead(jan2016reduc_olive,1) + jan2016reduc_olive + jan2017reduc + lead(jan2017reduc_olive,1) + jan2017reduc_olive + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow , data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

## nom price with significant lead and lags AND import interaction dummy

There was no setting under which the tuna 2015 and 2016 effects didn't create a dummy trap, so the two years were seperated in the case of tuna -->

```{r nom price with significant lead and lags and import, include=TRUE}
### TUNA
tuna$jan2015reduc_tuna_import <- tuna$jan2015reduc_tuna*tuna$import
tuna$jan2016reduc_tuna_import <- tuna$jan2015reduc_tuna*tuna$import
tuna_signif <- subset(tuna,date_n<382017)
tuna_net_lre_lags_sig_import_2015 <- plm(lprice_nom ~ jan2015reduc_tuna +  jan2015reduc_tuna_import, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig_import_2015, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
tuna_net_lre_lags_sig_import_2016 <- plm(lprice_nom ~ jan2016reduc_tuna +  jan2016reduc_tuna_import, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig_import_2016, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil$jan2016reduc_olive_import <- oil$jan2016reduc_olive*oil$import
oil$jan2017reduc_olive_import <- oil$jan2017reduc_olive*oil$import
oil_signif <- subset(oil,year<2018)
oil_net_lre_lags_sig_import <- plm(lprice_nom ~ jan2016reduc + jan2016reduc_olive +  lag(jan2016reduc_olive,3) + jan2016reduc_olive_import + jan2017reduc + jan2017reduc_olive + jan2017reduc_olive_import, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig_import, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese$jan2016reduc_yellow_import <- cheese$jan2016reduc_yellow*cheese$import
cheese$jan2017reduc_yellow_import <- cheese$jan2017reduc_yellow*cheese$import
cheese_net_lre_lags_sig_import <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + lag(jan2016reduc_yellow,1) + jan2016reduc_yellow_import+ jan2017reduc + jan2017reduc_yellow + lag(jan2017reduc_yellow,1) + jan2016reduc_yellow_import , data = cheese, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig_import, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

import as an interaction dummy was found not insignificant, and in tuna it was also ommitted due to linearity. import as a regular dummy deleted by the fixed effects estimation(?).



# Thesis Draft results

## diff-in-diff (Without import )

### regular model 

```{r regular , include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lags_sig <- plm(lprice_net ~ jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_full <- plm(lprice_net ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_full, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lags_sig <- plm(lprice_nom ~ jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lags_sig <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lags_sig <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's


# lprice_net
### TUNA
tuna_net_lre_lags_sig_X <- plm(lprice_net ~ jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_sig_X <- plm(lprice_net ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig_X <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lags_sig_X <- plm(lprice_nom ~ jan2015reduc_tuna + jan2016reduc + jan2016reduc_tuna+ proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lags_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lags_sig_X <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_olive + jan2017reduc + jan2017reduc_olive + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lags_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lags_sig_X <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2017reduc + jan2017reduc_yellow + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lags_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```
### lead 1

```{r only lead 1, include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lead_1_sig <- plm(lprice_net ~ lead(jan2015reduc_tuna,1) + lead(jan2016reduc,1) + lead(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lead_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lead_1_sig <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2016reduc_olive,1) + lead(jan2017reduc,1) + lead(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lead_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lead_1_sig <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2016reduc_yellow,1) + lead(jan2017reduc,1) + lead(jan2017reduc_yellow,1) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lead_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lead_1_sig <- plm(lprice_nom ~ lead(jan2015reduc_tuna,1) + lead(jan2016reduc,1) + lead(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lead_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lead_1_sig <- plm(lprice_nom ~  lead(jan2016reduc,1) + lead(jan2016reduc_olive,1) + lead(jan2017reduc,1) + lead(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lead_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lead_1_sig <- plm(lprice_nom ~  lead(jan2016reduc,1) + lead(jan2016reduc_yellow,1) + lead(jan2017reduc,1) + lead(jan2017reduc_yellow,1) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lead_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's

# lprice_net
### TUNA
tuna_net_lre_lead_1_sig_X <- plm(lprice_net ~ lead(jan2015reduc_tuna,1) + lead(jan2016reduc,1) + lead(jan2016reduc_tuna,1) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lead_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lead_1_sig_X <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2016reduc_olive,1) + lead(jan2017reduc,1) + lead(jan2017reduc_olive,1) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lead_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lead_1_sig_X <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2016reduc_yellow,1) + lead(jan2017reduc,1) + lead(jan2017reduc_yellow,1) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lead_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lead_1_sig_X <- plm(lprice_nom ~ lead(jan2015reduc_tuna,1) + lead(jan2016reduc,1) + lead(jan2016reduc_tuna,1) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lead_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lead_1_sig_X <- plm(lprice_nom ~  lead(jan2016reduc,1) + lead(jan2016reduc_olive,1) + lead(jan2017reduc,1) + lead(jan2017reduc_olive,1) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lead_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lead_1_sig_X <- plm(lprice_nom ~  lead(jan2016reduc,1) + lead(jan2016reduc_yellow,1) + lead(jan2017reduc,1) + lead(jan2017reduc_yellow,1) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker  , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lead_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

```

### lead_2

```{r only lead 2, include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lead_2_sig <- plm(lprice_net ~ lead(jan2015reduc_tuna,2) + lead(jan2016reduc,2) + lead(jan2016reduc_tuna,2), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lead_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lead_2_sig <- plm(lprice_net ~  lead(jan2016reduc,2) + lead(jan2016reduc_olive,2) + lead(jan2017reduc,2) + lead(jan2017reduc_olive,2), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lead_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lead_2_sig <- plm(lprice_net ~  lead(jan2016reduc,2) + lead(jan2016reduc_yellow,2) + lead(jan2017reduc,2) + lead(jan2017reduc_yellow,2) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lead_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lead_2_sig <- plm(lprice_nom ~ lead(jan2015reduc_tuna,2) + lead(jan2016reduc,2) + lead(jan2016reduc_tuna,2), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lead_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lead_2_sig <- plm(lprice_nom ~  lead(jan2016reduc,2) + lead(jan2016reduc_olive,2) + lead(jan2017reduc,2) + lead(jan2017reduc_olive,2), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lead_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lead_2_sig <- plm(lprice_nom ~  lead(jan2016reduc,2) + lead(jan2016reduc_yellow,2) + lead(jan2017reduc,2) + lead(jan2017reduc_yellow,2) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lead_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's

# lprice_net
### TUNA
tuna_net_lre_lead_2_sig_X <- plm(lprice_net ~ lead(jan2015reduc_tuna,2) + lead(jan2016reduc,2) + lead(jan2016reduc_tuna,2) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lead_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lead_2_sig_X <- plm(lprice_net ~  lead(jan2016reduc,2) + lead(jan2016reduc_olive,2) + lead(jan2017reduc,2) + lead(jan2017reduc_olive,2) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lead_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lead_2_sig_X <- plm(lprice_net ~  lead(jan2016reduc,2) + lead(jan2016reduc_yellow,2) + lead(jan2017reduc,2) + lead(jan2017reduc_yellow,2) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lead_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lead_2_sig_X <- plm(lprice_nom ~ lead(jan2015reduc_tuna,2) + lead(jan2016reduc,2) + lead(jan2016reduc_tuna,2) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lead_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lead_2_sig_X <- plm(lprice_nom ~  lead(jan2016reduc,2) + lead(jan2016reduc_olive,2) + lead(jan2017reduc,2) + lead(jan2017reduc_olive,2) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lead_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lead_2_sig_X <- plm(lprice_nom ~  lead(jan2016reduc,2) + lead(jan2016reduc_yellow,2) + lead(jan2017reduc,2) + lead(jan2017reduc_yellow,2) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker  , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lead_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

```

### lag_1

```{r only lag 1, include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lag_1_sig <- plm(lprice_net ~ lag(jan2015reduc_tuna,1) + lag(jan2016reduc,1) + lag(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_1_sig <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2016reduc_olive,1) + lag(jan2017reduc,1) + lag(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_1_sig <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2016reduc_yellow,1) + lag(jan2017reduc,1) + lag(jan2017reduc_yellow,1) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_1_sig <- plm(lprice_nom ~ lag(jan2015reduc_tuna,1) + lag(jan2016reduc,1) + lag(jan2016reduc_tuna,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_1_sig <- plm(lprice_nom ~  lag(jan2016reduc,1) + lag(jan2016reduc_olive,1) + lag(jan2017reduc,1) + lag(jan2017reduc_olive,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_1_sig <- plm(lprice_nom ~  lag(jan2016reduc,1) + lag(jan2016reduc_yellow,1) + lag(jan2017reduc,1) + lag(jan2017reduc_yellow,1) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_1_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's

# lprice_net
### TUNA
tuna_net_lre_lag_1_sig_X <- plm(lprice_net ~ lag(jan2015reduc_tuna,1) + lag(jan2016reduc,1) + lag(jan2016reduc_tuna,1) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_1_sig_X <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2016reduc_olive,1) + lag(jan2017reduc,1) + lag(jan2017reduc_olive,1) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_1_sig_X <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2016reduc_yellow,1) + lag(jan2017reduc,1) + lag(jan2017reduc_yellow,1) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_1_sig_X <- plm(lprice_nom ~ lag(jan2015reduc_tuna,1) + lag(jan2016reduc,1) + lag(jan2016reduc_tuna,1) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_1_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,1) + lag(jan2016reduc_olive,1) + lag(jan2017reduc,1) + lag(jan2017reduc_olive,1) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_1_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,1) + lag(jan2016reduc_yellow,1) + lag(jan2017reduc,1) + lag(jan2017reduc_yellow,1) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker  , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_1_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

```

### lag_2

```{r only lag 2, include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lag_2_sig <- plm(lprice_net ~ lag(jan2015reduc_tuna,2) + lag(jan2016reduc,2) + lag(jan2016reduc_tuna,2), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_2_sig <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2016reduc_olive,2) + lag(jan2017reduc,2) + lag(jan2017reduc_olive,2), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_2_sig <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2016reduc_yellow,2) + lag(jan2017reduc,2) + lag(jan2017reduc_yellow,2) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_2_sig <- plm(lprice_nom ~ lag(jan2015reduc_tuna,2) + lag(jan2016reduc,2) + lag(jan2016reduc_tuna,2), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_2_sig <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2016reduc_olive,2) + lag(jan2017reduc,2) + lag(jan2017reduc_olive,2), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_2_sig <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2016reduc_yellow,2) + lag(jan2017reduc,2) + lag(jan2017reduc_yellow,2) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_2_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's

# lprice_net
### TUNA
tuna_net_lre_lag_2_sig_X <- plm(lprice_net ~ lag(jan2015reduc_tuna,2) + lag(jan2016reduc,2) + lag(jan2016reduc_tuna,2) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_2_sig_X <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2016reduc_olive,2) + lag(jan2017reduc,2) + lag(jan2017reduc_olive,2) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_2_sig_X <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2016reduc_yellow,2) + lag(jan2017reduc,2) + lag(jan2017reduc_yellow,2) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_2_sig_X <- plm(lprice_nom ~ lag(jan2015reduc_tuna,2) + lag(jan2016reduc,2) + lag(jan2016reduc_tuna,2) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_2_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2016reduc_olive,2) + lag(jan2017reduc,2) + lag(jan2017reduc_olive,2) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_2_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2016reduc_yellow,2) + lag(jan2017reduc,2) + lag(jan2017reduc_yellow,2) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker  , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_2_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

```

### lag_3

```{r only lag 3, include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lag_3_sig <- plm(lprice_net ~ lag(jan2015reduc_tuna,3) + lag(jan2016reduc,3) + lag(jan2016reduc_tuna,3), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_3_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_3_sig <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2016reduc_olive,3) + lag(jan2017reduc,3) + lag(jan2017reduc_olive,3), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_3_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_3_sig <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2016reduc_yellow,3) + lag(jan2017reduc,3) + lag(jan2017reduc_yellow,3) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_3_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_3_sig <- plm(lprice_nom ~ lag(jan2015reduc_tuna,3) + lag(jan2016reduc,3) + lag(jan2016reduc_tuna,3), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_3_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_3_sig <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2016reduc_olive,3) + lag(jan2017reduc,3) + lag(jan2017reduc_olive,3), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_3_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_3_sig <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2016reduc_yellow,3) + lag(jan2017reduc,3) + lag(jan2017reduc_yellow,3) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_3_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's

# lprice_net
### TUNA
tuna_net_lre_lag_3_sig_X <- plm(lprice_net ~ lag(jan2015reduc_tuna,3) + lag(jan2016reduc,3) + lag(jan2016reduc_tuna,3) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_3_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_3_sig_X <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2016reduc_olive,3) + lag(jan2017reduc,3) + lag(jan2017reduc_olive,3) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_3_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_3_sig_X <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2016reduc_yellow,3) + lag(jan2017reduc,3) + lag(jan2017reduc_yellow,3) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_3_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_3_sig_X <- plm(lprice_nom ~ lag(jan2015reduc_tuna,3) + lag(jan2016reduc,3) + lag(jan2016reduc_tuna,3) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker
, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_3_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_3_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2016reduc_olive,3) + lag(jan2017reduc,3) + lag(jan2017reduc_olive,3) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_3_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_3_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2016reduc_yellow,3) + lag(jan2017reduc,3) + lag(jan2017reduc_yellow,3)
 + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker  , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_3_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

```

### lag_4

```{r only lag 4, include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lag_4_sig <- plm(lprice_net ~ lag(jan2015reduc_tuna,4) + lag(jan2016reduc,4) + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_4_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_4_sig <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2016reduc_olive,4) + lag(jan2017reduc,4) + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_4_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_4_sig <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2016reduc_yellow,4) + lag(jan2017reduc,4) + lag(jan2017reduc_yellow,4) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_4_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_4_sig <- plm(lprice_nom ~ lag(jan2015reduc_tuna,4) + lag(jan2016reduc,4) + lag(jan2016reduc_tuna,4), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_4_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_4_sig <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2016reduc_olive,4) + lag(jan2017reduc,4) + lag(jan2017reduc_olive,4), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_4_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_4_sig <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2016reduc_yellow,4) + lag(jan2017reduc,4) + lag(jan2017reduc_yellow,4) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_4_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's

# lprice_net
### TUNA
tuna_net_lre_lag_4_sig_X <- plm(lprice_net ~ lag(jan2015reduc_tuna,4) + lag(jan2016reduc,4) + lag(jan2016reduc_tuna,4) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_4_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_4_sig_X <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2016reduc_olive,4) + lag(jan2017reduc,4) + lag(jan2017reduc_olive,4) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_4_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_4_sig_X <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2016reduc_yellow,4) + lag(jan2017reduc,4) + lag(jan2017reduc_yellow,4) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_4_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_4_sig_X <- plm(lprice_nom ~ lag(jan2015reduc_tuna,4) + lag(jan2016reduc,4) + lag(jan2016reduc_tuna,4) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_4_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_4_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2016reduc_olive,4) + lag(jan2017reduc,4) + lag(jan2017reduc_olive,4) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_4_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_4_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2016reduc_yellow,4) + lag(jan2017reduc,4) + lag(jan2017reduc_yellow,4) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker  , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_4_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

```
### lag_5

```{r only lag 5, include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lag_5_sig <- plm(lprice_net ~ lag(jan2015reduc_tuna,5) + lag(jan2016reduc,5) + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_5_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_5_sig <- plm(lprice_net ~  lag(jan2016reduc,5) + lag(jan2016reduc_olive,5) + lag(jan2017reduc,5) + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_5_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_5_sig <- plm(lprice_net ~  lag(jan2016reduc,5) + lag(jan2016reduc_yellow,5) + lag(jan2017reduc,5) + lag(jan2017reduc_yellow,5) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_5_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_5_sig <- plm(lprice_nom ~ lag(jan2015reduc_tuna,5) + lag(jan2016reduc,5) + lag(jan2016reduc_tuna,5), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_5_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_5_sig <- plm(lprice_nom ~  lag(jan2016reduc,5) + lag(jan2016reduc_olive,5) + lag(jan2017reduc,5) + lag(jan2017reduc_olive,5), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_5_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_5_sig <- plm(lprice_nom ~  lag(jan2016reduc,5) + lag(jan2016reduc_yellow,5) + lag(jan2017reduc,5) + lag(jan2017reduc_yellow,5) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_5_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's

# lprice_net
### TUNA
tuna_net_lre_lag_5_sig_X <- plm(lprice_net ~ lag(jan2015reduc_tuna,5) + lag(jan2016reduc,5) + lag(jan2016reduc_tuna,5) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_5_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_5_sig_X <- plm(lprice_net ~  lag(jan2016reduc,5) + lag(jan2016reduc_olive,5) + lag(jan2017reduc,5) + lag(jan2017reduc_olive,5) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_5_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_5_sig_X <- plm(lprice_net ~  lag(jan2016reduc,5) + lag(jan2016reduc_yellow,5) + lag(jan2017reduc,5) + lag(jan2017reduc_yellow,5) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_5_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_5_sig_X <- plm(lprice_nom ~ lag(jan2015reduc_tuna,5) + lag(jan2016reduc,5) + lag(jan2016reduc_tuna,5) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_5_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_5_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,5) + lag(jan2016reduc_olive,5) + lag(jan2017reduc,5) + lag(jan2017reduc_olive,5) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_5_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_5_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,5) + lag(jan2016reduc_yellow,5) + lag(jan2017reduc,5) + lag(jan2017reduc_yellow,5) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker  , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_5_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

```

### lag_6

```{r only lag 6, include=TRUE}
# lprice_net
### TUNA
tuna_net_lre_lag_6_sig <- plm(lprice_net ~ lag(jan2015reduc_tuna,6) + lag(jan2016reduc,6) + lag(jan2016reduc_tuna,6), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_6_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_6_sig <- plm(lprice_net ~  lag(jan2016reduc,6) + lag(jan2016reduc_olive,6) + lag(jan2017reduc,6) + lag(jan2017reduc_olive,6), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_6_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_6_sig <- plm(lprice_net ~  lag(jan2016reduc,6) + lag(jan2016reduc_yellow,6) + lag(jan2017reduc,6) + lag(jan2017reduc_yellow,6) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_6_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_6_sig <- plm(lprice_nom ~ lag(jan2015reduc_tuna,6) + lag(jan2016reduc,6) + lag(jan2016reduc_tuna,6), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_6_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_6_sig <- plm(lprice_nom ~  lag(jan2016reduc,6) + lag(jan2016reduc_olive,6) + lag(jan2017reduc,6) + lag(jan2017reduc_olive,6), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_6_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_6_sig <- plm(lprice_nom ~  lag(jan2016reduc,6) + lag(jan2016reduc_yellow,6) + lag(jan2017reduc,6) + lag(jan2017reduc_yellow,6) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_6_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

# With X's

# lprice_net
### TUNA
tuna_net_lre_lag_6_sig_X <- plm(lprice_net ~ lag(jan2015reduc_tuna,6) + lag(jan2016reduc,6) + lag(jan2016reduc_tuna,6) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lag_6_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lag_6_sig_X <- plm(lprice_net ~  lag(jan2016reduc,6) + lag(jan2016reduc_olive,6) + lag(jan2017reduc,6) + lag(jan2017reduc_olive,6) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lag_6_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lag_6_sig_X <- plm(lprice_net ~  lag(jan2016reduc,6) + lag(jan2016reduc_yellow,6) + lag(jan2017reduc,6) + lag(jan2017reduc_yellow,6) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lag_6_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
# lprice_nom
### TUNA
tuna_nom_lre_lag_6_sig_X <- plm(lprice_nom ~ lag(jan2015reduc_tuna,6) + lag(jan2016reduc,6) + lag(jan2016reduc_tuna,6) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_nom_lre_lag_6_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_lag_6_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,6) + lag(jan2016reduc_olive,6) + lag(jan2017reduc,6) + lag(jan2017reduc_olive,6) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_nom_lre_lag_6_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_nom_lre_lag_6_sig_X <- plm(lprice_nom ~  lag(jan2016reduc,6) + lag(jan2016reduc_yellow,6) + lag(jan2017reduc,6) + lag(jan2017reduc_yellow,6)  + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_nom_lre_lag_6_sig_X, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

```

### create tables diff-in-diff
```{r create tables diff-in-diff , include=TRUE}
library(estout)

# append robust results function:
append_robust_results <- function(number,the_model,output_file) {
  robust_results<-data.frame(tidy(coeftest(the_model, vcov.=function(x) vcovHC(x,type="sss",cluster="group"))))
  write.table(number, output_file, sep = ",", col.names = !file.exists(output_file), append = T)
  write.table(robust_results, output_file, sep = ",", col.names = !file.exists(output_file), append = T)
}
### TUNA

output_file_name <- "tuna_diff_in_diff.reg"
output_file_name_csv <- paste0(output_file_name,'.csv')

eststo(tuna_nom_lre_lags_sig)
eststo(tuna_nom_lre_lead_1_sig)
eststo(tuna_nom_lre_lead_2_sig)
eststo(tuna_nom_lre_lag_1_sig)
eststo(tuna_nom_lre_lag_2_sig)
eststo(tuna_nom_lre_lag_3_sig)
eststo(tuna_nom_lre_lag_4_sig)
eststo(tuna_nom_lre_lag_5_sig)
eststo(tuna_nom_lre_lag_6_sig)
eststo(tuna_nom_lre_lags_sig_X)
eststo(tuna_nom_lre_lead_1_sig_X)
eststo(tuna_nom_lre_lead_2_sig_X)
eststo(tuna_nom_lre_lag_1_sig_X)
eststo(tuna_nom_lre_lag_2_sig_X)
eststo(tuna_nom_lre_lag_3_sig_X)
eststo(tuna_nom_lre_lag_4_sig_X)
eststo(tuna_nom_lre_lag_5_sig_X)
eststo(tuna_nom_lre_lag_6_sig_X)

eststo(tuna_net_lre_lags_sig)
eststo(tuna_net_lre_lead_1_sig)
eststo(tuna_net_lre_lead_2_sig)
eststo(tuna_net_lre_lag_1_sig)
eststo(tuna_net_lre_lag_2_sig)
eststo(tuna_net_lre_lag_3_sig)
eststo(tuna_net_lre_lag_4_sig)
eststo(tuna_net_lre_lag_5_sig)
eststo(tuna_net_lre_lag_6_sig)
eststo(tuna_net_lre_lags_sig_X)
eststo(tuna_net_lre_lead_1_sig_X)
eststo(tuna_net_lre_lead_2_sig_X)
eststo(tuna_net_lre_lag_1_sig_X)
eststo(tuna_net_lre_lag_2_sig_X)
eststo(tuna_net_lre_lag_3_sig_X)
eststo(tuna_net_lre_lag_4_sig_X)
eststo(tuna_net_lre_lag_5_sig_X)
eststo(tuna_net_lre_lag_6_sig_X)

# Output regression table
esttab(filename=output_file_name,csv=TRUE)
estclear()
# Append robust results
append_robust_results(1,tuna_nom_lre_lags_sig,output_file_name_csv)
append_robust_results(2,tuna_nom_lre_lead_1_sig,output_file_name_csv)
append_robust_results(3,tuna_nom_lre_lead_2_sig,output_file_name_csv)
append_robust_results(4,tuna_nom_lre_lag_1_sig,output_file_name_csv)
append_robust_results(5,tuna_nom_lre_lag_2_sig,output_file_name_csv)
append_robust_results(6,tuna_nom_lre_lag_3_sig,output_file_name_csv)
append_robust_results(7,tuna_nom_lre_lag_4_sig,output_file_name_csv)
append_robust_results(8,tuna_nom_lre_lag_5_sig,output_file_name_csv)
append_robust_results(9,tuna_nom_lre_lag_6_sig,output_file_name_csv)
append_robust_results(10,tuna_nom_lre_lags_sig_X,output_file_name_csv)
append_robust_results(11,tuna_nom_lre_lead_1_sig_X,output_file_name_csv)
append_robust_results(12,tuna_nom_lre_lead_2_sig_X,output_file_name_csv)
append_robust_results(13,tuna_nom_lre_lag_1_sig_X,output_file_name_csv)
append_robust_results(14,tuna_nom_lre_lag_2_sig_X,output_file_name_csv)
append_robust_results(15,tuna_nom_lre_lag_3_sig_X,output_file_name_csv)
append_robust_results(16,tuna_nom_lre_lag_4_sig_X,output_file_name_csv)
append_robust_results(17,tuna_nom_lre_lag_5_sig_X,output_file_name_csv)
append_robust_results(18,tuna_nom_lre_lag_6_sig_X,output_file_name_csv)

append_robust_results(19,tuna_net_lre_lags_sig,output_file_name_csv)
append_robust_results(20,tuna_net_lre_lead_1_sig,output_file_name_csv)
append_robust_results(21,tuna_net_lre_lead_2_sig,output_file_name_csv)
append_robust_results(22,tuna_net_lre_lag_1_sig,output_file_name_csv)
append_robust_results(23,tuna_net_lre_lag_2_sig,output_file_name_csv)
append_robust_results(24,tuna_net_lre_lag_3_sig,output_file_name_csv)
append_robust_results(25,tuna_net_lre_lag_4_sig,output_file_name_csv)
append_robust_results(26,tuna_net_lre_lag_5_sig,output_file_name_csv)
append_robust_results(27,tuna_net_lre_lag_6_sig,output_file_name_csv)
append_robust_results(28,tuna_net_lre_lags_sig_X,output_file_name_csv)
append_robust_results(29,tuna_net_lre_lead_1_sig_X,output_file_name_csv)
append_robust_results(30,tuna_net_lre_lead_2_sig_X,output_file_name_csv)
append_robust_results(31,tuna_net_lre_lag_1_sig_X,output_file_name_csv)
append_robust_results(32,tuna_net_lre_lag_2_sig_X,output_file_name_csv)
append_robust_results(33,tuna_net_lre_lag_3_sig_X,output_file_name_csv)
append_robust_results(34,tuna_net_lre_lag_4_sig_X,output_file_name_csv)
append_robust_results(35,tuna_net_lre_lag_5_sig_X,output_file_name_csv)
append_robust_results(36,tuna_net_lre_lag_6_sig_X,output_file_name_csv)

### oil

output_file_name <- "oil_diff_in_diff.reg"
output_file_name_csv <- paste0(output_file_name,'.csv')

eststo(oil_nom_lre_lags_sig)
eststo(oil_nom_lre_lead_1_sig)
eststo(oil_nom_lre_lead_2_sig)
eststo(oil_nom_lre_lag_1_sig)
eststo(oil_nom_lre_lag_2_sig)
eststo(oil_nom_lre_lag_3_sig)
eststo(oil_nom_lre_lag_4_sig)
eststo(oil_nom_lre_lag_5_sig)
eststo(oil_nom_lre_lag_6_sig)
eststo(oil_nom_lre_lags_sig_X)
eststo(oil_nom_lre_lead_1_sig_X)
eststo(oil_nom_lre_lead_2_sig_X)
eststo(oil_nom_lre_lag_1_sig_X)
eststo(oil_nom_lre_lag_2_sig_X)
eststo(oil_nom_lre_lag_3_sig_X)
eststo(oil_nom_lre_lag_4_sig_X)
eststo(oil_nom_lre_lag_5_sig_X)
eststo(oil_nom_lre_lag_6_sig_X)

eststo(oil_net_lre_lags_sig)
eststo(oil_net_lre_lead_1_sig)
eststo(oil_net_lre_lead_2_sig)
eststo(oil_net_lre_lag_1_sig)
eststo(oil_net_lre_lag_2_sig)
eststo(oil_net_lre_lag_3_sig)
eststo(oil_net_lre_lag_4_sig)
eststo(oil_net_lre_lag_5_sig)
eststo(oil_net_lre_lag_6_sig)
eststo(oil_net_lre_lags_sig_X)
eststo(oil_net_lre_lead_1_sig_X)
eststo(oil_net_lre_lead_2_sig_X)
eststo(oil_net_lre_lag_1_sig_X)
eststo(oil_net_lre_lag_2_sig_X)
eststo(oil_net_lre_lag_3_sig_X)
eststo(oil_net_lre_lag_4_sig_X)
eststo(oil_net_lre_lag_5_sig_X)
eststo(oil_net_lre_lag_6_sig_X)

# Output regression table
esttab(filename=output_file_name,csv=TRUE)
estclear()
# Append robust results
append_robust_results(1,oil_nom_lre_lags_sig,output_file_name_csv)
append_robust_results(2,oil_nom_lre_lead_1_sig,output_file_name_csv)
append_robust_results(3,oil_nom_lre_lead_2_sig,output_file_name_csv)
append_robust_results(4,oil_nom_lre_lag_1_sig,output_file_name_csv)
append_robust_results(5,oil_nom_lre_lag_2_sig,output_file_name_csv)
append_robust_results(6,oil_nom_lre_lag_3_sig,output_file_name_csv)
append_robust_results(7,oil_nom_lre_lag_4_sig,output_file_name_csv)
append_robust_results(8,oil_nom_lre_lag_5_sig,output_file_name_csv)
append_robust_results(9,oil_nom_lre_lag_6_sig,output_file_name_csv)
append_robust_results(10,oil_nom_lre_lags_sig_X,output_file_name_csv)
append_robust_results(11,oil_nom_lre_lead_1_sig_X,output_file_name_csv)
append_robust_results(12,oil_nom_lre_lead_2_sig_X,output_file_name_csv)
append_robust_results(13,oil_nom_lre_lag_1_sig_X,output_file_name_csv)
append_robust_results(14,oil_nom_lre_lag_2_sig_X,output_file_name_csv)
append_robust_results(15,oil_nom_lre_lag_3_sig_X,output_file_name_csv)
append_robust_results(16,oil_nom_lre_lag_4_sig_X,output_file_name_csv)
append_robust_results(17,oil_nom_lre_lag_5_sig_X,output_file_name_csv)
append_robust_results(18,oil_nom_lre_lag_6_sig_X,output_file_name_csv)

append_robust_results(19,oil_net_lre_lags_sig,output_file_name_csv)
append_robust_results(20,oil_net_lre_lead_1_sig,output_file_name_csv)
append_robust_results(21,oil_net_lre_lead_2_sig,output_file_name_csv)
append_robust_results(22,oil_net_lre_lag_1_sig,output_file_name_csv)
append_robust_results(23,oil_net_lre_lag_2_sig,output_file_name_csv)
append_robust_results(24,oil_net_lre_lag_3_sig,output_file_name_csv)
append_robust_results(25,oil_net_lre_lag_4_sig,output_file_name_csv)
append_robust_results(26,oil_net_lre_lag_5_sig,output_file_name_csv)
append_robust_results(27,oil_net_lre_lag_6_sig,output_file_name_csv)
append_robust_results(28,oil_net_lre_lags_sig_X,output_file_name_csv)
append_robust_results(29,oil_net_lre_lead_1_sig_X,output_file_name_csv)
append_robust_results(30,oil_net_lre_lead_2_sig_X,output_file_name_csv)
append_robust_results(31,oil_net_lre_lag_1_sig_X,output_file_name_csv)
append_robust_results(32,oil_net_lre_lag_2_sig_X,output_file_name_csv)
append_robust_results(33,oil_net_lre_lag_3_sig_X,output_file_name_csv)
append_robust_results(34,oil_net_lre_lag_4_sig_X,output_file_name_csv)
append_robust_results(35,oil_net_lre_lag_5_sig_X,output_file_name_csv)
append_robust_results(36,oil_net_lre_lag_6_sig_X,output_file_name_csv)

### Cheese


output_file_name <- "cheese_diff_in_diff.reg"
output_file_name_csv <- paste0(output_file_name,'.csv')

eststo(cheese_nom_lre_lags_sig)
eststo(cheese_nom_lre_lead_1_sig)
eststo(cheese_nom_lre_lead_2_sig)
eststo(cheese_nom_lre_lag_1_sig)
eststo(cheese_nom_lre_lag_2_sig)
eststo(cheese_nom_lre_lag_3_sig)
eststo(cheese_nom_lre_lag_4_sig)
eststo(cheese_nom_lre_lag_5_sig)
eststo(cheese_nom_lre_lag_6_sig)
eststo(cheese_nom_lre_lags_sig_X)
eststo(cheese_nom_lre_lead_1_sig_X)
eststo(cheese_nom_lre_lead_2_sig_X)
eststo(cheese_nom_lre_lag_1_sig_X)
eststo(cheese_nom_lre_lag_2_sig_X)
eststo(cheese_nom_lre_lag_3_sig_X)
eststo(cheese_nom_lre_lag_4_sig_X)
eststo(cheese_nom_lre_lag_5_sig_X)
eststo(cheese_nom_lre_lag_6_sig_X)

eststo(cheese_net_lre_lags_sig)
eststo(cheese_net_lre_lead_1_sig)
eststo(cheese_net_lre_lead_2_sig)
eststo(cheese_net_lre_lag_1_sig)
eststo(cheese_net_lre_lag_2_sig)
eststo(cheese_net_lre_lag_3_sig)
eststo(cheese_net_lre_lag_4_sig)
eststo(cheese_net_lre_lag_5_sig)
eststo(cheese_net_lre_lag_6_sig)
eststo(cheese_net_lre_lags_sig_X)
eststo(cheese_net_lre_lead_1_sig_X)
eststo(cheese_net_lre_lead_2_sig_X)
eststo(cheese_net_lre_lag_1_sig_X)
eststo(cheese_net_lre_lag_2_sig_X)
eststo(cheese_net_lre_lag_3_sig_X)
eststo(cheese_net_lre_lag_4_sig_X)
eststo(cheese_net_lre_lag_5_sig_X)
eststo(cheese_net_lre_lag_6_sig_X)

# Output regression table
esttab(filename=output_file_name,csv=TRUE)
estclear()
# Append robust results
append_robust_results(1,cheese_nom_lre_lags_sig,output_file_name_csv)
append_robust_results(2,cheese_nom_lre_lead_1_sig,output_file_name_csv)
append_robust_results(3,cheese_nom_lre_lead_2_sig,output_file_name_csv)
append_robust_results(4,cheese_nom_lre_lag_1_sig,output_file_name_csv)
append_robust_results(5,cheese_nom_lre_lag_2_sig,output_file_name_csv)
append_robust_results(6,cheese_nom_lre_lag_3_sig,output_file_name_csv)
append_robust_results(7,cheese_nom_lre_lag_4_sig,output_file_name_csv)
append_robust_results(8,cheese_nom_lre_lag_5_sig,output_file_name_csv)
append_robust_results(9,cheese_nom_lre_lag_6_sig,output_file_name_csv)
append_robust_results(10,cheese_nom_lre_lags_sig_X,output_file_name_csv)
append_robust_results(11,cheese_nom_lre_lead_1_sig_X,output_file_name_csv)
append_robust_results(12,cheese_nom_lre_lead_2_sig_X,output_file_name_csv)
append_robust_results(13,cheese_nom_lre_lag_1_sig_X,output_file_name_csv)
append_robust_results(14,cheese_nom_lre_lag_2_sig_X,output_file_name_csv)
append_robust_results(15,cheese_nom_lre_lag_3_sig_X,output_file_name_csv)
append_robust_results(16,cheese_nom_lre_lag_4_sig_X,output_file_name_csv)
append_robust_results(17,cheese_nom_lre_lag_5_sig_X,output_file_name_csv)
append_robust_results(18,cheese_nom_lre_lag_6_sig_X,output_file_name_csv)

append_robust_results(19,cheese_net_lre_lags_sig,output_file_name_csv)
append_robust_results(20,cheese_net_lre_lead_1_sig,output_file_name_csv)
append_robust_results(21,cheese_net_lre_lead_2_sig,output_file_name_csv)
append_robust_results(22,cheese_net_lre_lag_1_sig,output_file_name_csv)
append_robust_results(23,cheese_net_lre_lag_2_sig,output_file_name_csv)
append_robust_results(24,cheese_net_lre_lag_3_sig,output_file_name_csv)
append_robust_results(25,cheese_net_lre_lag_4_sig,output_file_name_csv)
append_robust_results(26,cheese_net_lre_lag_5_sig,output_file_name_csv)
append_robust_results(27,cheese_net_lre_lag_6_sig,output_file_name_csv)
append_robust_results(28,cheese_net_lre_lags_sig_X,output_file_name_csv)
append_robust_results(29,cheese_net_lre_lead_1_sig_X,output_file_name_csv)
append_robust_results(30,cheese_net_lre_lead_2_sig_X,output_file_name_csv)
append_robust_results(31,cheese_net_lre_lag_1_sig_X,output_file_name_csv)
append_robust_results(32,cheese_net_lre_lag_2_sig_X,output_file_name_csv)
append_robust_results(33,cheese_net_lre_lag_3_sig_X,output_file_name_csv)
append_robust_results(34,cheese_net_lre_lag_4_sig_X,output_file_name_csv)
append_robust_results(35,cheese_net_lre_lag_5_sig_X,output_file_name_csv)
append_robust_results(36,cheese_net_lre_lag_6_sig_X,output_file_name_csv)
```

## diff-in-diff-in-diff (With import)

```{r regular diff-in-diff , include=TRUE}
# create different datasets for every year, since we are unable to run both tarrif reductions together
## 1st tarrif reduction:
tuna_signif_before_2016 <- subset(tuna_signif,year<2016)
oil_signif_before_2017 <- subset(oil_signif,year<2017)
cheese_signif_before_2017 <- subset(cheese_signif,year<2017)
## 2st tarrif reduction:
tuna_signif_after_2014 <- subset(tuna_signif,year>2014)
oil_signif_after_2015 <- subset(oil_signif,year>2015)
cheese_signif_after_2015 <- subset(cheese_signif,year>2015)
##lprice_net
### TUNA
tuna_net_lre_import_2015 <- plm(lprice_net ~ jan2015reduc + jan2015reduc_tuna +  jan2015reduc_tuna_import, data = tuna_signif_before_2016, effect="twoways",model = "random")
coeftest(tuna_net_lre_import_2015, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
tuna_net_lre_import_2016 <- plm(lprice_net ~ jan2016reduc + jan2016reduc_tuna +  jan2016reduc_tuna_import, data = tuna_signif_after_2014, effect="twoways",model = "random")
coeftest(tuna_net_lre_import_2016, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_import_2016 <- plm(lprice_net ~  jan2016reduc + jan2016reduc_olive + jan2016reduc_olive_import, data = oil_signif_before_2017, effect="twoways",model = "random")
coeftest(oil_net_lre_import_2016, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_net_lre_import_2017 <- plm(lprice_net ~  jan2017reduc + jan2017reduc_olive + jan2017reduc_olive_import, data = oil_signif_after_2015, effect="twoways",model = "random")
coeftest(oil_net_lre_import_2017, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### cheese
cheese_net_lre_import_2016 <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2016reduc_yellow_import, data = cheese_signif_signif_before_2017, effect="twoways",model = "random")
coeftest(cheese_net_lre_import_2016, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_net_lre_import_2017 <- plm(lprice_net ~  jan2017reduc + jan2017reduc_yellow + jan2017reduc_yellow_import, data = cheese_signif_signif_after_2015, effect="twoways",model = "random")
coeftest(cheese_net_lre_import_2017, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))

##lprice_nom
### TUNA
tuna_nom_lre_import_2015 <- plm(lprice_nom ~ jan2015reduc + jan2015reduc_tuna +  jan2015reduc_tuna_import, data = tuna_signif_before_2016, effect="twoways",model = "random")
coeftest(tuna_nom_lre_import_2015, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
tuna_nom_lre_import_2016 <- plm(lprice_nom ~ jan2016reduc + jan2016reduc_tuna +  jan2016reduc_tuna_import, data = tuna_signif_after_2014, effect="twoways",model = "random")
coeftest(tuna_nom_lre_import_2016, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_nom_lre_import_2016 <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_olive + jan2016reduc_olive_import, data = oil_signif_before_2017, effect="twoways",model = "random")
coeftest(oil_nom_lre_import_2016, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
oil_nom_lre_import_2017 <- plm(lprice_nom ~  jan2017reduc + jan2017reduc_olive + jan2017reduc_olive_import, data = oil_signif_after_2015, effect="twoways",model = "random")
coeftest(oil_nom_lre_import_2017, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### cheese
cheese_nom_lre_import_2016 <- plm(lprice_nom ~  jan2016reduc + jan2016reduc_yellow + jan2016reduc_yellow_import, data = cheese_signif_signif_before_2017, effect="twoways",model = "random")
coeftest(cheese_nom_lre_import_2016, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
cheese_nom_lre_import_2017 <- plm(lprice_nom ~  jan2017reduc + jan2017reduc_yellow + jan2017reduc_yellow_import, data = cheese_signif_signif_after_2015, effect="twoways",model = "random")
coeftest(cheese_nom_lre_import_2017, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))



```




### regular model 

```{r regular with import , include=TRUE}
### TUNA
tuna_net_lre_lags_sig <- plm(lprice_net ~ jan2015reduc_tuna  + jan2016reduc + jan2016reduc_tuna + jan2016reduc_tuna_import, data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_sig <- plm(lprice_net ~  jan2016reduc + jan2016reduc_olive + jan2016reduc_olive_import + jan2017reduc + jan2017reduc_olive + jan2017reduc_olive_import, data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig <- plm(lprice_net ~  jan2016reduc + jan2016reduc_yellow + jan2016reduc_yellow_import + jan2017reduc + jan2017reduc_yellow + jan2016reduc_yellow_import, data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

## Only lag 1

```{r only lag 1 with import, include=TRUE}
### TUNA
tuna_net_lre_lags_sig <- plm(lprice_net ~ lag(jan2015reduc_tuna,1)  + lag(jan2016reduc,1) + lag(jan2016reduc_tuna,1) + lag(jan2016reduc_tuna_import,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_sig <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2016reduc_olive,1) + lag(jan2016reduc_olive_import,1) + lag(jan2017reduc,1) + lag(jan2017reduc_olive,1) + lag(jan2017reduc_olive_import,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2016reduc_yellow,1) + lag(jan2016reduc_yellow_import,1) + lag(jan2017reduc,1) + lag(jan2017reduc_yellow,1) + lag(jan2016reduc_yellow_import,1), data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

## Only Lead

```{r only lead with import, include=TRUE}
### TUNA
tuna_net_lre_lags_sig <- plm(lprice_net ~ lead(jan2015reduc_tuna,1) + lead(jan2016reduc,1) + lead(jan2016reduc_tuna,1) + lead(jan2016reduc_tuna_import,1), data = tuna_signif, effect="twoways",model = "random")
coeftest(tuna_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
### OIL
oil_net_lre_lags_sig <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2016reduc_olive,1) + + lead(jan2016reduc_olive_import,1) + lead(jan2017reduc,1) + lead(jan2017reduc_olive,1) + lead(jan2017reduc_olive_import,1), data = oil_signif, effect="twoways",model = "random") 
coeftest(oil_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
## Cheese
cheese_net_lre_lags_sig <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2016reduc_yellow,1) + lead(jan2016reduc_yellow_import,1) + lead(jan2017reduc,1) + lead(jan2017reduc_yellow,1) + lead(jan2016reduc_yellow_import,1) , data = cheese_signif, effect="twoways",model = "random")
coeftest(cheese_net_lre_lags_sig, vcov.=function(x) vcovHC(x, type="sss",cluster="group"))
```

# Simple model


```{r simple model tuna random effects , include=TRUE}
library(estout)

# append robust results function:
append_robust_results <- function(number,the_model,output_file) {
  robust_results<-data.frame(tidy(coeftest(the_model, vcov.=function(x) vcovHC(x,type="sss",cluster="group"))))
  write.table(number, output_file, sep = ",", col.names = !file.exists(output_file), append = T)
  write.table(robust_results, output_file, sep = ",", col.names = !file.exists(output_file), append = T)
}


output_file_name <- "tuna_simple.reg"
output_file_name_csv <- paste0(output_file_name,'.csv')

estclear()

# Tuna pre-process
tuna_without_sardin <- subset(tuna_signif,!(sardin==1))
tuna_without_sardin$lsalary_industry_worker<-log(tuna_without_sardin$salary_industry_worker)

## 1. price not full 
tuna_without_sardin_model1 <- plm(lprice_nom ~  jan2015reduc + jan2016reduc, data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model1)
## 2. price 1 lead not full
tuna_without_sardin_model2 <- plm(lprice_nom ~  lead(jan2015reduc,1) + lead(jan2016reduc,1), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model2)
## 3. price 2 lead not full
tuna_without_sardin_model3 <- plm(lprice_nom ~  lead(jan2015reduc,2) + lead(jan2016reduc,2), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model3)
## 4. price not full 1 lag
tuna_without_sardin_model4 <- plm(lprice_nom ~  lag(jan2015reduc,1) + lag(jan2016reduc,1), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model4)
## 5. price not full 2 lag
tuna_without_sardin_model5 <- plm(lprice_nom ~  lag(jan2015reduc,2) + lag(jan2016reduc,2), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model5)
## 6. price not full 3 lag
tuna_without_sardin_model6 <- plm(lprice_nom ~  lag(jan2015reduc,3) + lag(jan2016reduc,3), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model6)
## 7. price not full 4 lag
tuna_without_sardin_model7 <- plm(lprice_nom ~  lag(jan2015reduc,4) + lag(jan2016reduc,4), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model7)
## 8. price not full 5 lag
tuna_without_sardin_model8 <- plm(lprice_nom ~  lag(jan2015reduc,5) + lag(jan2016reduc,5), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model8)
## 9. price not full 6 lag
tuna_without_sardin_model9 <- plm(lprice_nom ~  lag(jan2015reduc,6) + lag(jan2016reduc,6), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model9)

## 10. price full 
tuna_without_sardin_model10 <- plm(lprice_nom ~  jan2015reduc + jan2016reduc + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model10)
## 11. price 1 lead full
tuna_without_sardin_model11 <- plm(lprice_nom ~  lead(jan2015reduc,1) + lead(jan2016reduc,1) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model11)
## 12. price 2 lead full
tuna_without_sardin_model12 <- plm(lprice_nom ~  lead(jan2015reduc,2) + lead(jan2016reduc,2) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model12)
## 13. price full 1 lag
tuna_without_sardin_model13 <- plm(lprice_nom ~  lag(jan2015reduc,1) + lag(jan2016reduc,1) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model13)
## 14. price full 2 lag
tuna_without_sardin_model14 <- plm(lprice_nom ~  lag(jan2015reduc,2) + lag(jan2016reduc,2) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model14)
## 15. price full 3 lag
tuna_without_sardin_model15 <- plm(lprice_nom ~  lag(jan2015reduc,3) + lag(jan2016reduc,3) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model15)
## 16. price full 4 lag
tuna_without_sardin_model16 <- plm(lprice_nom ~  lag(jan2015reduc,4) + lag(jan2016reduc,4) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model16)
## 17. price full 5 lag
tuna_without_sardin_model17 <- plm(lprice_nom ~  lag(jan2015reduc,5) + lag(jan2016reduc,5) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model17)
## 18. price full 6 lag
tuna_without_sardin_model18 <- plm(lprice_nom ~  lag(jan2015reduc,6) + lag(jan2016reduc,6) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model18)

## 19. price_net not full 
tuna_without_sardin_model19 <- plm(lprice_net ~  jan2015reduc + jan2016reduc, data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model19)
## 20. price_net 2 lead not full
tuna_without_sardin_model20 <- plm(lprice_net ~  lead(jan2015reduc,2) + lead(jan2016reduc,2), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model20)
## 21. price_net 1 lead not full
tuna_without_sardin_model21 <- plm(lprice_net ~  lead(jan2015reduc,1) + lead(jan2016reduc,1), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model21)
## 22. price_net not full 1 lag
tuna_without_sardin_model22 <- plm(lprice_net ~  lag(jan2015reduc,1) + lag(jan2016reduc,1), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model22)
## 23. price_net not full 2 lag
tuna_without_sardin_model23 <- plm(lprice_net ~  lag(jan2015reduc,2) + lag(jan2016reduc,2), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model23)
## 24. price_net not full 3 lag
tuna_without_sardin_model24 <- plm(lprice_net ~  lag(jan2015reduc,3) + lag(jan2016reduc,3), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model24)
## 25. price_net not full 4 lag
tuna_without_sardin_model25 <- plm(lprice_net ~  lag(jan2015reduc,4) + lag(jan2016reduc,4), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model25)
## 26. price_net not full 5 lag
tuna_without_sardin_model26 <- plm(lprice_net ~  lag(jan2015reduc,5) + lag(jan2016reduc,5), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model26)
## 27. price_net not full 6 lag
tuna_without_sardin_model27 <- plm(lprice_net ~  lag(jan2015reduc,6) + lag(jan2016reduc,6), data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model27)

## 28. price_net full 
tuna_without_sardin_model28 <- plm(lprice_net ~  jan2015reduc + jan2016reduc + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model28)
## 29. price_net 2 lead full
tuna_without_sardin_model29 <- plm(lprice_net ~  lead(jan2015reduc,2) + lead(jan2016reduc,2) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model29)
## 30. price_net 1 lead full
tuna_without_sardin_model30 <- plm(lprice_net ~  lead(jan2015reduc,1) + lead(jan2016reduc,1) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model30)
## 31. price_net full 1 lag
tuna_without_sardin_model31 <- plm(lprice_net ~  lag(jan2015reduc,1) + lag(jan2016reduc,1) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model31)
## 32. price_net full 2 lag
tuna_without_sardin_model32 <- plm(lprice_net ~  lag(jan2015reduc,2) + lag(jan2016reduc,2) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model32)
## 33. price_net full 3 lag
tuna_without_sardin_model33 <- plm(lprice_net ~  lag(jan2015reduc,3) + lag(jan2016reduc,3) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model33)
## 34. price_net full 4 lag
tuna_without_sardin_model34 <- plm(lprice_net ~  lag(jan2015reduc,4) + lag(jan2016reduc,4) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model34)
## 35. price_net full 5 lag
tuna_without_sardin_model35 <- plm(lprice_net ~  lag(jan2015reduc,5) + lag(jan2016reduc,5) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model35)
## 36. price_net full 6 lag
tuna_without_sardin_model36 <- plm(lprice_net ~  lag(jan2015reduc,6) + lag(jan2016reduc,6) + proccess_fish_p2012 + lvalue_added_tax + lsalary_industry_worker , data = tuna_without_sardin, effect="individual",model = "random")
eststo(tuna_without_sardin_model36)

# Output regression table
esttab(filename=output_file_name,csv=TRUE)
estclear()
# Append robust results
for (i in 1:36) {
 append_robust_results(i,get(paste0("tuna_without_sardin_model",i)),output_file_name_csv)
}


```


```{r simple model oil random effects , include=TRUE}
library(estout)

output_file_name <- "oilasdasdasd_simple.reg"
output_file_name_csv <- paste0(output_file_name,'.csv')

estclear()

# oil pre-process
oil_without_canola <- subset(oil_signif,!(cooking_oil==1))
oil_without_canola$lsalary_industry_worker<-log(oil_without_canola$salary_industry_worker)

## 1. price not full 
oil_without_canola_model1 <- plm(lprice_nom ~  jan2016reduc + jan2017reduc, data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model1)
## 2. price 1 lead not full
oil_without_canola_model2 <- plm(lprice_nom ~  lead(jan2016reduc,1) + lead(jan2017reduc,1), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model2)
## 3. price 2 lead not full
oil_without_canola_model3 <- plm(lprice_nom ~  lead(jan2016reduc,2) + lead(jan2017reduc,2), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model3)
## 4. price not full 1 lag
oil_without_canola_model4 <- plm(lprice_nom ~  lag(jan2016reduc,1) + lag(jan2017reduc,1), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model4)
## 5. price not full 2 lag
oil_without_canola_model5 <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2017reduc,2), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model5)
## 6. price not full 3 lag
oil_without_canola_model6 <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2017reduc,3), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model6)
## 7. price not full 4 lag
oil_without_canola_model7 <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2017reduc,4), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model7)
## 8. price not full 5 lag
oil_without_canola_model8 <- plm(lprice_nom ~  lag(jan2016reduc,5) + lag(jan2017reduc,5), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model8)
## 9. price not full 6 lag
oil_without_canola_model9 <- plm(lprice_nom ~  lag(jan2016reduc,6) + lag(jan2017reduc,6), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model9)

## 10. price full 
oil_without_canola_model10 <- plm(lprice_nom ~  jan2016reduc + jan2017reduc + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model10)
## 11. price 1 lead full
oil_without_canola_model11 <- plm(lprice_nom ~  lead(jan2016reduc,1) + lead(jan2017reduc,1) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model11)
## 12. price 2 lead full
oil_without_canola_model12 <- plm(lprice_nom ~  lead(jan2016reduc,2) + lead(jan2017reduc,2) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model12)
## 13. price full 1 lag
oil_without_canola_model13 <- plm(lprice_nom ~  lag(jan2016reduc,1) + lag(jan2017reduc,1) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model13)
## 14. price full 2 lag
oil_without_canola_model14 <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2017reduc,2) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model14)
## 15. price full 3 lag
oil_without_canola_model15 <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2017reduc,3) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model15)
## 16. price full 4 lag
oil_without_canola_model16 <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2017reduc,4) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model16)
## 17. price full 5 lag
oil_without_canola_model17 <- plm(lprice_nom ~  lag(jan2016reduc,5) + lag(jan2017reduc,5) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model17)
## 18. price full 6 lag
oil_without_canola_model18 <- plm(lprice_nom ~  lag(jan2016reduc,6) + lag(jan2017reduc,6) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model18)

## 19. price_net not full 
oil_without_canola_model19 <- plm(lprice_net ~  jan2016reduc + jan2017reduc, data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model19)
## 20. price_net 2 lead not full
oil_without_canola_model20 <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2017reduc,1), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model20)
## 21. price_net 1 lead not full
oil_without_canola_model21 <- plm(lprice_net ~  lead(jan2016reduc,2) + lead(jan2017reduc,2), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model21)
## 22. price_net not full 1 lag
oil_without_canola_model22 <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2017reduc,1), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model22)
## 23. price_net not full 2 lag
oil_without_canola_model23 <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2017reduc,2), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model23)
## 24. price_net not full 3 lag
oil_without_canola_model24 <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2017reduc,3), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model24)
## 25. price_net not full 4 lag
oil_without_canola_model25 <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2017reduc,4), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model25)
## 26. price_net not full 5 lag
oil_without_canola_model26 <- plm(lprice_net ~  lag(jan2016reduc,5) + lag(jan2017reduc,5), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model26)
## 27. price_net not full 6 lag
oil_without_canola_model27 <- plm(lprice_net ~  lag(jan2016reduc,6) + lag(jan2017reduc,6), data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model27)

## 28. price_net full 
oil_without_canola_model28 <- plm(lprice_net ~  jan2016reduc + jan2017reduc + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model28)
## 29. price_net 2 lead full
oil_without_canola_model29 <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2017reduc,2) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model29)
## 30. price_net 1 lead full
oil_without_canola_model30 <- plm(lprice_net ~  lead(jan2016reduc,2) + lead(jan2017reduc,1) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model30)
## 31. price_net full 1 lag
oil_without_canola_model31 <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2017reduc,1) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model31)
## 32. price_net full 2 lag
oil_without_canola_model32 <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2017reduc,2) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model32)
## 33. price_net full 3 lag
oil_without_canola_model33 <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2017reduc,3) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model33)
## 34. price_net full 4 lag
oil_without_canola_model34 <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2017reduc,4) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model34)
## 35. price_net full 5 lag
oil_without_canola_model35 <- plm(lprice_net ~  lag(jan2016reduc,5) + lag(jan2017reduc,5) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model35)
## 36. price_net full 6 lag
oil_without_canola_model36 <- plm(lprice_net ~  lag(jan2016reduc,6) + lag(jan2017reduc,6) + proccess_oil_p2012 + lvalue_added_tax + lsalary_industry_worker , data = oil_without_canola, effect="individual",model = "random")
eststo(oil_without_canola_model36)

# Output regression table
esttab(filename=output_file_name,csv=TRUE)
estclear()
# Append robust results
for (i in 1:36) {
 append_robust_results(i,get(paste0("oil_without_canola_model",i)),output_file_name_csv)
}


```

```{r simple model cheese random effects , include=TRUE}
library(estout)

output_file_name <- "cheese_simple.reg"
output_file_name_csv <- paste0(output_file_name,'.csv')

estclear()

# cheese pre-process
#cheese_signif <- subset(cheese,date_n<382017)
cheese_without_white_cheese <- subset(cheese_signif,!(white_cheese==1))
cheese_without_white_cheese$lsalary_industry_worker<-log(cheese_without_white_cheese$salary_industry_worker)


## 1. price not full 
cheese_without_white_cheese_model1 <- plm(lprice_nom ~  jan2016reduc + jan2017reduc, data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model1)
## 2. price 1 lead not full
cheese_without_white_cheese_model2 <- plm(lprice_nom ~  lead(jan2016reduc,1) + lead(jan2017reduc,1), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model2)
## 3. price 2 lead not full
cheese_without_white_cheese_model3 <- plm(lprice_nom ~  lead(jan2016reduc,2) + lead(jan2017reduc,2), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model3)
## 4. price not full 1 lag
cheese_without_white_cheese_model4 <- plm(lprice_nom ~  lag(jan2016reduc,1) + lag(jan2017reduc,1), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model4)
## 5. price not full 2 lag
cheese_without_white_cheese_model5 <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2017reduc,2), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model5)
## 6. price not full 3 lag
cheese_without_white_cheese_model6 <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2017reduc,3), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model6)
## 7. price not full 4 lag
cheese_without_white_cheese_model7 <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2017reduc,4), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model7)
## 8. price not full 5 lag
cheese_without_white_cheese_model8 <- plm(lprice_nom ~  lag(jan2016reduc,5) + lag(jan2017reduc,5), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model8)
## 9. price not full 6 lag
cheese_without_white_cheese_model9 <- plm(lprice_nom ~  lag(jan2016reduc,6) + lag(jan2017reduc,6), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model9)

## 10. price full 
cheese_without_white_cheese_model10 <- plm(lprice_nom ~  jan2016reduc + jan2017reduc + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model10)
## 11. price 1 lead full
cheese_without_white_cheese_model11 <- plm(lprice_nom ~  lead(jan2016reduc,1) + lead(jan2017reduc,1) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model11)
## 12. price 2 lead full
cheese_without_white_cheese_model12 <- plm(lprice_nom ~  lead(jan2016reduc,2) + lead(jan2017reduc,2) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model12)
## 13. price full 1 lag
cheese_without_white_cheese_model13 <- plm(lprice_nom ~  lag(jan2016reduc,1) + lag(jan2017reduc,1) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model13)
## 14. price full 2 lag
cheese_without_white_cheese_model14 <- plm(lprice_nom ~  lag(jan2016reduc,2) + lag(jan2017reduc,2) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model14)
## 15. price full 3 lag
cheese_without_white_cheese_model15 <- plm(lprice_nom ~  lag(jan2016reduc,3) + lag(jan2017reduc,3) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model15)
## 16. price full 4 lag
cheese_without_white_cheese_model16 <- plm(lprice_nom ~  lag(jan2016reduc,4) + lag(jan2017reduc,4) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model16)
## 17. price full 5 lag
cheese_without_white_cheese_model17 <- plm(lprice_nom ~  lag(jan2016reduc,5) + lag(jan2017reduc,5) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model17)
## 18. price full 6 lag
cheese_without_white_cheese_model18 <- plm(lprice_nom ~  lag(jan2016reduc,6) + lag(jan2017reduc,6) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model18)

## 19. price_net not full 
cheese_without_white_cheese_model19 <- plm(lprice_net ~  jan2016reduc + jan2017reduc, data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model19)
## 20. price_net 2 lead not full
cheese_without_white_cheese_model20 <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2017reduc,1), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model20)
## 21. price_net 1 lead not full
cheese_without_white_cheese_model21 <- plm(lprice_net ~  lead(jan2016reduc,2) + lead(jan2017reduc,2), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model21)
## 22. price_net not full 1 lag
cheese_without_white_cheese_model22 <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2017reduc,1), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model22)
## 23. price_net not full 2 lag
cheese_without_white_cheese_model23 <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2017reduc,2), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model23)
## 24. price_net not full 3 lag
cheese_without_white_cheese_model24 <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2017reduc,3), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model24)
## 25. price_net not full 4 lag
cheese_without_white_cheese_model25 <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2017reduc,4), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model25)
## 26. price_net not full 5 lag
cheese_without_white_cheese_model26 <- plm(lprice_net ~  lag(jan2016reduc,5) + lag(jan2017reduc,5), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model26)
## 27. price_net not full 6 lag
cheese_without_white_cheese_model27 <- plm(lprice_net ~  lag(jan2016reduc,6) + lag(jan2017reduc,6), data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model27)

## 28. price_net full 
cheese_without_white_cheese_model28 <- plm(lprice_net ~  jan2016reduc + jan2017reduc + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model28)
## 29. price_net 1 lead full
cheese_without_white_cheese_model29 <- plm(lprice_net ~  lead(jan2016reduc,1) + lead(jan2017reduc,1) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model29)
## 30. price_net 2 lead full
cheese_without_white_cheese_model30 <- plm(lprice_net ~  lead(jan2016reduc,2) + lead(jan2017reduc,2) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model30)
## 31. price_net full 1 lag
cheese_without_white_cheese_model31 <- plm(lprice_net ~  lag(jan2016reduc,1) + lag(jan2017reduc,1) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model31)
## 32. price_net full 2 lag
cheese_without_white_cheese_model32 <- plm(lprice_net ~  lag(jan2016reduc,2) + lag(jan2017reduc,2) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model32)
## 33. price_net full 3 lag
cheese_without_white_cheese_model33 <- plm(lprice_net ~  lag(jan2016reduc,3) + lag(jan2017reduc,3) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model33)
## 34. price_net full 4 lag
cheese_without_white_cheese_model34 <- plm(lprice_net ~  lag(jan2016reduc,4) + lag(jan2017reduc,4) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model34)
## 35. price_net full 5 lag
cheese_without_white_cheese_model35 <- plm(lprice_net ~  lag(jan2016reduc,5) + lag(jan2017reduc,5) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model35)
## 36. price_net full 6 lag
cheese_without_white_cheese_model36 <- plm(lprice_net ~  lag(jan2016reduc,6) + lag(jan2017reduc,6) + proccess_milk_products_p2012+ lvalue_added_tax + lsalary_industry_worker , data = cheese_signif_without_white_cheese, effect="individual",model = "random")
eststo(cheese_without_white_cheese_model36)

# Output regression table
esttab(filename=output_file_name,csv=TRUE)
estclear()
# Append robust results
for (i in 1:36) {
 append_robust_results(i,get(paste0("cheese_without_white_cheese_model",i)),output_file_name_csv)
}


```

```{r diff-in-diff model tuna random effects , include=TRUE}
library(estout)

output_file_name <- "tuna_diff.reg"
output_file_name_csv <- paste0(output_file_name,'.csv')

estclear()

eststo(tuna_nom_lre_lags_sig)
eststo(tuna_nom_lre_lead_1_sig)
eststo(tuna_nom_lre_lead_2_sig)
eststo(tuna_nom_lre_lag_1_sig)
eststo(tuna_nom_lre_lag_2_sig)
eststo(tuna_nom_lre_lag_3_sig)
eststo(tuna_nom_lre_lag_4_sig)
eststo(tuna_nom_lre_lag_5_sig)
eststo(tuna_nom_lre_lag_6_sig)

eststo(tuna_net_lre_lags_sig)
eststo(tuna_net_lre_lead_1_sig)
eststo(tuna_net_lre_lead_2_sig)
eststo(tuna_net_lre_lag_1_sig)
eststo(tuna_net_lre_lag_2_sig)
eststo(tuna_net_lre_lag_3_sig)
eststo(tuna_net_lre_lag_4_sig)
eststo(tuna_net_lre_lag_5_sig)
eststo(tuna_net_lre_lag_6_sig)

# Output regression table
esttab(filename=output_file_name,csv=TRUE)
estclear()
# Append robust results
for (i in 1:36) {
 append_robust_results(i,get(paste0("tuna_diff_model",i)),output_file_name_csv)
}


```